---
title: "CM Syntax Review #3 - Internship Paper"
author: "ReJoyce Green"
output:
  word_document:
    toc: true
  pdf_document:
    toc: true
    latex_engine: xelatex
editor_options:
  chunk_output_type: console
---

# Overview
+ Syntax from CM 'Concordance Paper Syntax Updated 3..txt' file. 
+ RG changes: 
  + minor formatting changes to take syntax from .txt to .Rmd
  + major changes are indicated in syntax ('RG NOTE') and in notes section of syntax

# Data wrangling 

## Create final dataset based on inclusion criteria
+ Inclusion criteria #1
  + sufficient data present to create concordance variable from Community Risk 
    and Protective Factors Survey (CRPF) either alcohol or cannabis 
    - data needed for youth AND parent report for CRPF - alcohol questions 0R
    - data needed for youth AND parent report for CRPF - cannabis 
 + note: 
   - criteria for youth to be administered these questions is having heard
     of alcohol or cannabis at the 2-year timepoint
   - therefore, we can assume that all have heard of either alcohol or 
     or cannabis if they have meet this 1st inclusion criteria 

+ Inclusion criteria #2
  + attended 30-month or 3-year visit 
    - based on inclusion criteria #1, we know all have heard of alcohol OR
      cannabis 

```{r eval = FALSE}
# load relevant packages
library(dplyr)
library(tidyr)
library(broom)
library(tidyverse)
library(psych)
library(DescTools)
library(Hmisc)
library(mice)
library(ggplot2)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(mitml)
library(rcompanion)
library(performance)
library(car)
library(DHARMa)
library(summarytools)
library(gtsummary)
library(rstatix)
library(doParallel)
library(doRNG)
library(plotly)


#------------------------------------------------------------------------------#
#                         Inclusion Criteria #1
#------------------------------------------------------------------------------#

# import CRPF parent and youth data
su_p_crpf <- read_csv('data/su_p_crpf.csv') %>%
  subset(eventname == '2_year_follow_up_y_arm_1') %>%
  select(src_subject_id, su_risk_p_1, su_risk_p_4)

su_y_crpf <- read_csv('data/su_y_crpf.csv') %>%
  subset(eventname == '2_year_follow_up_y_arm_1') %>%
  select(src_subject_id, su_crpf_avail_1, su_crpf_avail_4)
  
# merge into single dataframe
crpf <- su_p_crpf %>%
  full_join(su_y_crpf, by = 'src_subject_id')
  
rm(su_p_crpf, su_y_crpf)

table(crpf$su_risk_p_1, useNA = 'ifany')
table(crpf$su_risk_p_4, useNA = 'ifany')
table(crpf$su_crpf_avail_1, useNA = 'ifany')
table(crpf$su_crpf_avail_4, useNA = 'ifany')

#--- RG NOTE:
# - As a general note, it may be helpful to get a breakdown of the number of 
#   values recoded from 777 or 999 to NA to include in supplemental materials. 
#--- RG NOTE:

# recode values of 'Don't Know' 
crpf <- crpf %>%
  mutate(
    across(
      .cols = starts_with('su_risk'),
      .fns = ~ ifelse(.x == 4, NA, .x)))
      
crpf <- crpf %>%
  mutate(
    across(
      .cols = starts_with('su_crpf'),
      .fns = ~ ifelse(.x == 999, NA, .x)))

table(crpf$su_risk_p_1, useNA = 'ifany')
table(crpf$su_risk_p_4, useNA = 'ifany')
table(crpf$su_crpf_avail_1, useNA = 'ifany')
table(crpf$su_crpf_avail_4, useNA = 'ifany')      
      
# create single concordance variable
crpf <- crpf %>%
  mutate(
    # cannabis
    crpf_p_cb = case_when(
      su_risk_p_4 == 0 | su_risk_p_4 == 1 ~ 'Hard',
      su_risk_p_4 == 2 | su_risk_p_4 == 3 ~ 'Easy'),
    crpf_y_cb = case_when(
      su_crpf_avail_4 == 1 | su_crpf_avail_4 == 2 ~ 'Hard',
      su_crpf_avail_4 == 3 | su_crpf_avail_4 == 4 ~ 'Easy'),
    # alcohol
    crpf_p_alc = case_when(
      su_risk_p_1 == 0 | su_risk_p_1 == 1 ~ 'Hard',
      su_risk_p_1 == 2 | su_risk_p_1 == 3 ~ 'Easy'),
    crpf_y_alc = case_when(
      su_crpf_avail_1 == 1 | su_crpf_avail_1 == 2 ~ 'Hard',
      su_crpf_avail_1 == 3 | su_crpf_avail_1 == 4 ~ 'Easy')) %>% 
  mutate(
    crpf_p_cb = as.factor(crpf_p_cb),
    crpf_y_cb = as.factor(crpf_y_cb),
    crpf_p_alc = as.factor(crpf_p_alc),
    crpf_y_alc = as.factor(crpf_y_alc)) %>% 
  mutate(
    cc_cb = case_when(
      crpf_p_cb == 'Hard' & crpf_y_cb == 'Hard' ~ 'Concordance Limited C',
      crpf_p_cb == 'Easy' & crpf_y_cb == 'Easy' ~ 'Concordance Unlimited C',
      crpf_p_cb == 'Hard' & crpf_y_cb == 'Easy' ~ 'Discordance Unlimted C',
      crpf_p_cb == 'Easy' & crpf_y_cb == 'Hard' ~ 'Discordance Limited C'),
    cc_alc = case_when(
      crpf_p_alc == 'Hard' & crpf_y_alc == 'Hard' ~ 'Concordance Limited A',
      crpf_p_alc == 'Easy' & crpf_y_alc == 'Easy' ~ 'Concordance Unlimited A',
      crpf_p_alc == 'Hard' & crpf_y_alc == 'Easy' ~ 'Discordance Unlimted A',
      crpf_p_alc == 'Easy' & crpf_y_alc == 'Hard' ~ 'Discordance Limited A'))
      
# only include those who have concordance variable for alcohol OR cannabis
table(crpf$cc_cb, useNA = 'ifany')
table(crpf$cc_alc, useNA = 'ifany')
table(crpf$cc_cb, crpf$cc_alc, useNA = 'ifany') 
# n = 2032 missing concordance on alcohol AND cannabis to be excluded 

crpf <- crpf %>% 
  subset(!is.na(cc_cb) | !is.na(cc_alc)) 
# expected n: original (10962) - to be dropped (2032) = 8930

# retain only required variables for final dataset
crpf <- crpf %>% 
  select(src_subject_id, cc_cb, cc_alc) %>% 
  mutate(
    cc_cb = as.factor(cc_cb),
    cc_alc = as.factor(cc_alc))
  
# begin creating final dataset
df_final <- crpf %>%
  select(src_subject_id, cc_cb, cc_alc)
  
# proportion missing concordance results
table(df_final$cc_cb, useNA = 'ifany')
table(df_final$cc_alc, useNA = 'ifany')

#descriptive
describe(df_final$cc_cb)
describe(df_final$cc_alc)

rm(crpf)

#------------------------------------------------------------------------------#
#                         Inclusion Criteria #2
#------------------------------------------------------------------------------#

# import longitudinal tracking data

IC_2 <- read_csv('data/abcd_y_lt.csv') %>% 
  subset(
    eventname == '30_month_follow_up_arm_1' |
      eventname == '3_year_follow_up_y_arm_1') %>% 
  select(src_subject_id, eventname) %>% 
  pivot_wider(id_cols = 'src_subject_id',
              names_from = 'eventname',
              names_sep = ".",
              values_from = c(eventname)) %>% 
  rename(
    visit_30m = '30_month_follow_up_arm_1',
    visit_3y = '3_year_follow_up_y_arm_1') %>% 
  # create variable to indicate attended 30-m, 3-y, or 30-m
  mutate(
    visit_att = case_when(
      !is.na(visit_30m) & !is.na(visit_3y) ~ 'Visit: 30-month & 3-year',
      !is.na(visit_30m) & is.na(visit_3y) ~ 'Visit: 30-month only',
      is.na(visit_30m) & !is.na(visit_3y) ~ 'Visit: 3-year only')) %>% 
  select(src_subject_id, visit_att)

# n = 10932 in IC_2
# - 10,932 higher than n at 3-yr follow-up in 5.1 release notes
#   to be expected given we are also including those who attended the 30-month
#   but did not attend the 3-year

# merge w/existing final dataset
df_final <- df_final %>% 
  left_join(IC_2, by = 'src_subject_id') 

# drop those who did not attend 30-month or 3-year
table(df_final$visit_att, useNA = 'ifany')
# n = 217 did not attend 3-year as indicated by missing data
  
df_final <- df_final %>% 
  subset(!is.na(visit_att))

rm(IC_2)

#--- Final Sample Size ---#
# n = 10973
#   - initial sample size for 2-year in 5.1 release notes
# n = 10962
#   - data present for parent or youth CRPF (sample size of crpf dataframe)
# n = 8930
#   - met inclusion criteria #1: data present for creating concordance 
#     variable at 2-year follow-up
# n = 8713
#   - met inclusion criteria #2: attended 30-month or 3-year visit to create
#     initiation outcome
#--- Final Sample Size ---#

# create dataset that only contains ID for final sample

df_final_ID <- df_final %>% 
  select(src_subject_id)

#--- RG NOTE:
# - I like to create a dataframe that only has IDs for the final sample. This
#   way when I am starting to create summary scores for variables later on,
#   and I want to subset to only include those in my final sample to see how
#   the number of 777s I am changing to NA for example, I have an easy way to
#   subset the dataframe based on these final IDs

```


## Create summary scores for relevant variables

+ Outcome
  + (1) Substance use initiation 
    + Based on the updates to the inclusion criteria, we can assume that all who have data for alcohol concordance
      have heard of alcohol, and that all who have data present for cannabis concordance have heard of cannabis. Therefore,
      previous inclusion criteria of having data present for 'heard of' alcohol or cannabis has been addressed with inclusion
      criteria #1. 
    + Lingering item to address: if someone did not indicate substance use at 30-month and did not attend 3-year, I would suggest 
      not including them in the SU initiation models on the basis that they could have initiated at the 3-year mark but we do not
      know. 
  + (2) Expectancies
    + Using pre-calculated summary scores where data must be present for all individual items for summary score to be created. 
  + (3) Perceptions of Harm
    + Creating summary scores defined as a sum of 3 items. Using all data available (i.e., if data present for only 2 individual
      items, then final summary score reflects sum of those 2 items).
    + Included a breakdown of the IDs that had data present for all 3 items, 2 items, or 1 item (for alcohol and cannabis, 
      respectively). If missing data on all 3 individual items, then final summary score coded as 'NA' (previously was being
      coded as 0)
  
+ Covariates



```{r eval = FALSE}

#------------------------------------------------------------------------------#
#                 Substance Initiation: Alcohol and Cannabis 
#------------------------------------------------------------------------------#

# import substance use (SU) data at baseline and follow-up
su_yr <- read_csv('data/su_y_sui.csv') %>%
  subset(eventname != '4_year_follow_up_y_arm_1') %>%
  select(
    src_subject_id, eventname,
    # baseline
    tlfb_alc_sip, isip_1b_yn, tlfb_mj_puff, tlfb_blunt_use, tlfb_mj_conc_use, 
    tlfb_mj_drink_use, tlfb_tincture_use,
    # yearly follow-up
    tlfb_alc_sip_l, isip_1b_yn_l, tlfb_mj_puff_l, tlfb_blunt_use_l, 
    tlfb_mj_conc_use_l, tlfb_mj_drink_use_l, tlfb_tincture_use_l,
    # gating criteria
    tlfb_alc, tlfb_alc_l, tlfb_mj, tlfb_mj_l) %>%
mutate(eventname = case_when(
  eventname == 'baseline_year_1_arm_1' ~ 'baseline',
  eventname == '1_year_follow_up_y_arm_1' ~ '1_year',
  eventname == '2_year_follow_up_y_arm_1' ~ '2_year',
  eventname == '3_year_follow_up_y_arm_1' ~ '3_year'))

# import substance use data at mid-year timepoints
su_mid <- read_csv('data/su_y_mypi.csv') %>%
subset(eventname != '42_month_follow_up_arm_1') %>%
  select(
    src_subject_id, eventname,
    mypi_alc_sip, mypi_alc_sip_1b, mypi_mj_used, mypi_mj_edible, mypi_mj_oils,
    mypi_mj_tinc_used, mypi_mj_vape, mypi_mj_oils_vaped,
#gating criteria
    mypi_alc, mypi_mj) %>%
  mutate(eventname = case_when(
    eventname == '6_month_follow_up_arm_1' ~ '6_month',
    eventname == '18_month_follow_up_arm_1' ~ '18_month',
    eventname == '30_month_follow_up_arm_1' ~ '30_month'))

# transpose from long to wide
su_yr_wide <- su_yr %>%
  pivot_wider(id_cols = 'src_subject_id',
              names_from = 'eventname',
              names_sep = ".",
              values_from = c(
                tlfb_alc_sip, isip_1b_yn,
                tlfb_alc_sip_l, isip_1b_yn_l,
                tlfb_alc, tlfb_alc_l, tlfb_mj_puff, tlfb_blunt_use,
                tlfb_mj_conc_use, tlfb_mj_drink_use,
                tlfb_tincture_use,tlfb_mj_puff_l, tlfb_blunt_use_l,
                tlfb_mj_conc_use_l, tlfb_mj_drink_use_l,
                tlfb_tincture_use_l, tlfb_mj,tlfb_mj_l))

su_mid_wide <- su_mid %>%
  pivot_wider(id_cols = 'src_subject_id',
              names_from = 'eventname',
              names_sep = ".",
              values_from = c(
                mypi_alc_sip, mypi_alc_sip_1b, mypi_alc, 
                mypi_mj_used, mypi_mj_edible, mypi_mj_oils, mypi_mj_tinc_used,
                mypi_mj_vape, mypi_mj_oils_vaped, mypi_mj))
                              
df_sub <- su_yr_wide %>%
  full_join(su_mid_wide, by = 'src_subject_id')

# subset SU data to only include IDs in final dataset
df_sub <- df_sub %>% 
  right_join(df_final_ID, by = 'src_subject_id')

# recode values of 777 as missing at mid-year timepoints
df_sub <- df_sub %>%
  mutate(
    across(.cols = starts_with('mypi_') & ends_with('.6_month'),
           .fns = ~replace(.x, .x == 777, NA))) %>%
  mutate(
    across(.cols = starts_with('mypi_') & ends_with('.18_month'),
           .fns = ~replace(.x, .x == 777, NA))) %>%
  mutate(
    across(.cols = starts_with('mypi_') & ends_with('.30_month'),
           .fns = ~replace(.x, .x == 777, NA)))
           
# general inclusion criteria: completed 2-year follow-up
# - checked by checking for age at 2-year follow-up
# su_yr <- read_csv('data/su_y_sui.csv') %>%
#   arrange(src_subject_id) %>%
#   subset(eventname == '2_year_follow_up_y_arm_1') %>%
#   select(src_subject_id, tlfb_age_l) %>%
#   rename(tlfb_age_l_2y = tlfb_age_l)

# df_sub <- temp %>%
#   subset(!is.na(tlfb_age_l_2y))

# temp <- df_sub %>%
#   left_join(su_yr, by = 'src_subject_id')

# rm(temp, su_yr)

#--- RG NOTE:
# - I commented out the syntax above for checking who completed the 2-year 
#   follow-up b/c I have created a final substance use dataset that only
#   includes those who met the 2 inclusion criteria, so we know they attended
#   the 2-year follow-up
#--- RG NOTE:

#----------
# Create SU initiation variables
#----------

# (1) exclude if initiation at baseline, 6m, 1y, 18m, or 2y

df_sub <- df_sub %>%
  mutate(
    alc_base = case_when(
      isip_1b_yn.baseline == 1 ~ 1,
      isip_1b_yn.baseline == 0 ~ 0,
      is.na(isip_1b_yn.baseline) ~ 0),
    alc_6m = case_when(
      mypi_alc_sip_1b.6_month == 1 ~ 1,
      mypi_alc_sip_1b.6_month == 0 ~ 0,
      is.na(mypi_alc_sip_1b.6_month) ~ 0),
    alc_1y = case_when(
      isip_1b_yn_l.1_year == 1 ~ 1,
      isip_1b_yn_l.1_year == 0 ~ 0,
      is.na(isip_1b_yn_l.1_year) ~ 0),
    alc_18m = case_when(
      mypi_alc_sip_1b.18_month == 1 ~ 1,
      mypi_alc_sip_1b.18_month == 0 ~ 0,
      is.na(mypi_alc_sip_1b.18_month) ~ 0),
    alc_2y = case_when(
      isip_1b_yn_l.2_year == 1 ~ 1,
      isip_1b_yn_l.2_year == 0 ~ 0,
      is.na(isip_1b_yn_l.2_year) ~ 0)) %>% 
  mutate(
    cb_base_mj_puff = case_when(
      tlfb_mj_puff.baseline == 1 ~ 1,
      tlfb_mj_puff.baseline == 0 ~ 0,
      is.na(tlfb_mj_puff.baseline) ~ 0),
    cb_base_blunt_use = case_when(
      tlfb_blunt_use.baseline == 1 ~ 1,
      tlfb_blunt_use.baseline == 0 ~ 0,
      is.na(tlfb_blunt_use.baseline) ~ 0),
    cb_base_mj_conc_use = case_when(
      tlfb_mj_conc_use.baseline == 1 ~ 1,
      tlfb_mj_conc_use.baseline == 0 ~ 0,
      is.na(tlfb_mj_conc_use.baseline) ~ 0),
    cb_base_mj_drink_use = case_when(
      tlfb_mj_drink_use.baseline == 1 ~ 1,
      tlfb_mj_drink_use.baseline == 0 ~ 0,
      is.na(tlfb_mj_drink_use.baseline) ~ 0),
    cb_base_tincture_use = case_when(
      tlfb_tincture_use.baseline == 1 ~ 1,
      tlfb_tincture_use.baseline == 0 ~ 0,
      is.na(tlfb_tincture_use.baseline) ~ 0),

    cb_6m_mj_used = case_when(
      mypi_mj_used.6_month == 1 ~ 1,
      mypi_mj_used.6_month == 0 ~ 0,
      is.na(mypi_mj_used.6_month) ~ 0),
    cb_6m_mj_edible = case_when(
      mypi_mj_edible.6_month == 1 ~ 1,
      mypi_mj_edible.6_month == 0 ~ 0,
      is.na(mypi_mj_edible.6_month) ~ 0),
    cb_6m_mj_oils = case_when(
      mypi_mj_oils.6_month == 1 ~ 1,
      mypi_mj_oils.6_month == 0 ~ 0,
      is.na(mypi_mj_oils.6_month) ~ 0),
    cb_6m_mj_tinc_used = case_when(
      mypi_mj_tinc_used.6_month == 1 ~ 1,
      mypi_mj_tinc_used.6_month == 0 ~ 0,
      is.na(mypi_mj_tinc_used.6_month) ~ 0),
    cb_6m_mj_vape = case_when(
      mypi_mj_vape.6_month == 1 ~ 1,
      mypi_mj_tinc_used.6_month == 0 ~ 0,
      is.na(mypi_mj_tinc_used.6_month) ~ 0),
    cb_6m_mj_oils_vaped = case_when(
      mypi_mj_oils_vaped.6_month == 1 ~ 1,
      mypi_mj_oils_vaped.6_month == 0 ~ 0,
      is.na(mypi_mj_oils_vaped.6_month) ~ 0),

    cb_1y_mj_puff = case_when(
      tlfb_mj_puff_l.1_year == 1 ~ 1,
      tlfb_mj_puff_l.1_year == 0 ~ 0,
      is.na(tlfb_mj_puff_l.1_year) ~ 0),
    cb_1y_blunt_use = case_when(
      tlfb_blunt_use_l.1_year == 1 ~ 1,
      tlfb_blunt_use_l.1_year == 0 ~ 0,
      is.na(tlfb_blunt_use_l.1_year) ~ 0),
    cb_1y_mj_conc_use = case_when(
      tlfb_mj_conc_use_l.1_year == 1 ~ 1,
      tlfb_mj_conc_use_l.1_year == 0 ~ 0,
      is.na(tlfb_mj_conc_use_l.1_year) ~ 0),
    cb_1y_mj_drink_use = case_when(
      tlfb_mj_drink_use_l.1_year == 1 ~ 1,
      tlfb_mj_drink_use_l.1_year == 0 ~ 0,
      is.na(tlfb_mj_drink_use_l.1_year) ~ 0),
    cb_1y_tincture_use = case_when(
      tlfb_tincture_use_l.1_year == 1 ~ 1,
      tlfb_tincture_use_l.1_year == 0 ~ 0,
      is.na(tlfb_tincture_use_l.1_year) ~ 0),

    cb_18m_mj_used = case_when(
      mypi_mj_used.18_month == 1 ~ 1,
      mypi_mj_used.18_month == 0 ~ 0,
      is.na(mypi_mj_used.18_month) ~ 0),
    cb_18m_mj_edible = case_when(
      mypi_mj_edible.18_month == 1 ~ 1,
      mypi_mj_edible.18_month == 0 ~ 0,
      is.na(mypi_mj_edible.18_month) ~ 0),
    cb_18m_mj_oils = case_when(
      mypi_mj_oils.18_month == 1 ~ 1,
      mypi_mj_oils.18_month == 0 ~ 0,
      is.na(mypi_mj_oils.18_month) ~ 0),
    cb_18m_mj_tinc_used = case_when(
      mypi_mj_tinc_used.18_month == 1 ~ 1,
      mypi_mj_tinc_used.18_month == 0 ~ 0,
      is.na(mypi_mj_tinc_used.18_month) ~ 0),
    cb_18m_mj_vape = case_when(
      mypi_mj_vape.18_month == 1 ~ 1,
      mypi_mj_tinc_used.18_month == 0 ~ 0,
      is.na(mypi_mj_tinc_used.18_month) ~ 0),
    cb_18m_mj_oils_vaped = case_when(
      mypi_mj_oils_vaped.18_month == 1 ~ 1,
      mypi_mj_oils_vaped.18_month == 0 ~ 0,
      is.na(mypi_mj_oils_vaped.18_month) ~ 0),

    cb_2y_mj_puff = case_when(
      tlfb_mj_puff_l.2_year == 1 ~ 1,
      tlfb_mj_puff_l.2_year == 0 ~ 0,
      is.na(tlfb_mj_puff_l.2_year) ~ 0),
    cb_2y_blunt_use = case_when(
      tlfb_blunt_use_l.2_year == 1 ~ 1,
      tlfb_blunt_use_l.2_year == 0 ~ 0,
      is.na(tlfb_blunt_use_l.2_year) ~ 0),
    cb_2y_mj_conc_use = case_when(
      tlfb_mj_conc_use_l.2_year == 1 ~ 1,
      tlfb_mj_conc_use_l.2_year == 0 ~ 0,
      is.na(tlfb_mj_conc_use_l.2_year) ~ 0),
    cb_2y_mj_drink_use = case_when(
      tlfb_mj_drink_use_l.2_year == 1 ~ 1,
      tlfb_mj_drink_use_l.2_year == 0 ~ 0,
      is.na(tlfb_mj_drink_use_l.2_year) ~ 0),
    cb_2y_tincture_use = case_when(
      tlfb_tincture_use_l.2_year == 1 ~ 1,
      tlfb_tincture_use_l.2_year == 0 ~ 0,
      is.na(tlfb_tincture_use_l.2_year) ~ 0)) %>% 
  mutate(
    cb_base = ifelse(
      cb_base_mj_puff == 1 | cb_base_blunt_use == 1 |
        cb_base_mj_conc_use == 1 | cb_base_mj_drink_use == 1 |
        cb_base_tincture_use == 1, 1, 0),
    
    cb_6m = ifelse(
      cb_6m_mj_used == 1 | cb_6m_mj_edible == 1 | cb_6m_mj_oils == 1 |
        cb_6m_mj_tinc_used == 1 | cb_6m_mj_vape == 1 |
        cb_6m_mj_oils_vaped == 1, 1, 0),
    
    cb_1y = ifelse(
      cb_1y_mj_puff == 1 | cb_1y_blunt_use == 1 | 
        cb_1y_mj_conc_use == 1 | cb_1y_mj_drink_use == 1 |
        cb_1y_tincture_use == 1, 1, 0),
    
    cb_18m = ifelse(
      cb_18m_mj_used == 1 | cb_18m_mj_edible == 1 | cb_18m_mj_oils == 1 |
        cb_18m_mj_tinc_used == 1 | cb_18m_mj_vape == 1 |
        cb_18m_mj_oils_vaped == 1, 1, 0),
    
    cb_2y = ifelse(
      cb_2y_mj_puff == 1 | cb_2y_blunt_use == 1 |
        cb_2y_mj_conc_use == 1 | cb_2y_mj_drink_use == 1 |
        cb_2y_tincture_use == 1, 1, 0))

table(df_sub$alc_base, useNA = 'ifany')
table(df_sub$alc_6m, useNA = 'ifany')
table(df_sub$alc_1y, useNA = 'ifany')
table(df_sub$alc_18m, useNA = 'ifany')
table(df_sub$alc_2y, useNA = 'ifany')

table(df_sub$cb_base, useNA = 'ifany')
table(df_sub$cb_6m, useNA = 'ifany')
table(df_sub$cb_1y, useNA = 'ifany')
table(df_sub$cb_18m, useNA = 'ifany')
table(df_sub$cb_2y, useNA = 'ifany')

write.csv(df_sub, 'output/df_sub.csv')
write.csv(su_mid, 'output/su_mid.csv')
write.csv(su_yr, 'output/su_yr.csv')

alc_base <- table(df_sub$alc_base, useNA = 'ifany')
capture.output(alc_base, file = 'output/alc_base.txt')

alc_6m <- table(df_sub$alc_6m, useNA = 'ifany')
capture.output(alc_6m, file = 'output/alc_6m.txt')

alc_1y <- table(df_sub$alc_1y, useNA = 'ifany')
capture.output(alc_1y, file = 'output/alc_1y.txt')

alc_18m <- table(df_sub$alc_18m, useNA = 'ifany')
capture.output(alc_18m, file = 'output/alc_18m.txt')

alc_2y <- table(df_sub$alc_2y, useNA = 'ifany')
capture.output(alc_2y, file = 'output/alc_2y.txt')

cb_base <- table(df_sub$cb_base, useNA = 'ifany')
capture.output(cb_base, file = 'output/cb_base.txt')

cb_6m <- table(df_sub$cb_6m, useNA = 'ifany')
capture.output(cb_6m, file = 'output/cb_6m.txt')

cb_1y <- table(df_sub$cb_1y, useNA = 'ifany')
capture.output(cb_1y, file = 'output/cb_1y.txt')

cb_18m <- table(df_sub$cb_18m, useNA = 'ifany')
capture.output(cb_18m, file = 'output/cb_18m.txt')

cb_2y <- table(df_sub$cb_2y, useNA = 'ifany')
capture.output(cb_2y, file = 'output/cb_2y.txt')

# (2) create binary initiation variable at 30m & 3y

df_sub <- df_sub %>%
  mutate(
    # alcohol
    DV_alc_30m = case_when(
      mypi_alc_sip_1b.30_month == 1 ~ 1,
      mypi_alc_sip_1b.30_month == 0 ~ 0,
      is.na(mypi_alc_sip_1b.30_month) ~ 0),
    DV_alc_3y = case_when(
      isip_1b_yn_l.3_year == 1 ~ 1,
      isip_1b_yn_l.3_year == 0 ~ 0,
      is.na(isip_1b_yn.3_year) ~ 0),
    
    # cannabis
    cb_30m_mj_used = case_when(
      mypi_mj_used.30_month == 1 ~ 1,
      mypi_mj_used.30_month == 0 ~ 0,
      is.na(mypi_mj_used.30_month) ~ 0),
    cb_30m_mj_edible = case_when(
      mypi_mj_edible.30_month == 1 ~ 1,
      mypi_mj_edible.30_month == 0 ~ 0,
      is.na(mypi_mj_edible.30_month) ~ 0),
    cb_30m_mj_oils = case_when(
      mypi_mj_oils.30_month == 1 ~ 1,
      mypi_mj_oils.30_month == 0 ~ 0,
      is.na(mypi_mj_oils.30_month) ~ 0),
    cb_30m_mj_tinc_used = case_when(
      mypi_mj_tinc_used.30_month == 1 ~ 1,
      mypi_mj_tinc_used.30_month == 0 ~ 0,
      is.na(mypi_mj_tinc_used.30_month) ~ 0),
    cb_30m_mj_vape = case_when(
      mypi_mj_vape.30_month == 1 ~ 1,
      mypi_mj_tinc_used.30_month == 0 ~ 0,
      is.na(mypi_mj_tinc_used.30_month) ~ 0),
    cb_30m_mj_oils_vaped = case_when(
      mypi_mj_oils_vaped.30_month == 1 ~ 1,
      mypi_mj_oils_vaped.30_month == 0 ~ 0,
      is.na(mypi_mj_oils_vaped.30_month) ~ 0),
      
    cb_3y_mj_puff = case_when(
      tlfb_mj_puff_l.3_year == 1 ~ 1,
      tlfb_mj_puff_l.3_year == 0 ~ 0,
      is.na(tlfb_mj_puff_l.3_year) ~ 0),
    cb_3y_blunt_use = case_when(
      tlfb_blunt_use_l.3_year == 1 ~ 1,
      tlfb_blunt_use_l.3_year == 0 ~ 0,
      is.na(tlfb_blunt_use_l.3_year) ~ 0),
    cb_3y_mj_conc_use = case_when(  
      tlfb_mj_conc_use_l.3_year == 1 ~ 1,
      tlfb_mj_conc_use_l.3_year == 0 ~ 0,
      is.na(tlfb_mj_conc_use_l.3_year) ~ 0),
    cb_3y_mj_drink_use = case_when(
      tlfb_mj_drink_use_l.3_year == 1 ~ 1,
      tlfb_mj_drink_use_l.3_year == 0 ~ 0,
      is.na(tlfb_mj_drink_use_l.3_year) ~ 0),
    cb_3y_tincture_use = case_when(
      tlfb_tincture_use_l.3_year == 1 ~ 1,
      tlfb_tincture_use_l.3_year == 0 ~ 0,
      is.na(tlfb_tincture_use_l.3_year) ~ 0),
  
    DV_cb_30m = ifelse(
      cb_30m_mj_used == 1 | cb_30m_mj_edible == 1 | cb_30m_mj_oils == 1 |
      cb_30m_mj_tinc_used == 1 | cb_30m_mj_vape == 1 |
      cb_30m_mj_oils_vaped == 1, 1, 0),
    DV_cb_3y = ifelse(
      cb_3y_mj_puff == 1 | cb_3y_blunt_use == 1 |
      cb_3y_mj_conc_use == 1 | cb_3y_mj_drink_use == 1 |
      cb_3y_tincture_use == 1, 1, 0)) %>% 
  mutate(
    DV_alc = case_when(
      alc_base == 1 | alc_6m == 1 | alc_1y == 1 | alc_18m == 1 | alc_2y == 1 ~ 'Excluded due to prior initiation',
      DV_alc_30m == 1 | DV_alc_3y == 1 ~ 'Yes',
      DV_alc_30m == 0 & DV_alc_3y == 0 ~ 'No'),
    DV_alc = as.factor(DV_alc),
    DV_cb = case_when(
      cb_base == 1 | cb_6m == 1 | cb_1y == 1 | cb_18m == 1 | cb_2y == 1 ~ 'Excluded due to prior initiation',
      DV_cb_30m == 1 | DV_cb_3y == 1 ~ 'Yes',
      DV_cb_30m == 0 & DV_cb_3y == 0 ~ 'No'),
    DV_cb = as.factor(DV_cb))

table(df_sub$DV_alc_30m, useNA = 'ifany')
table(df_sub$DV_alc_3y, useNA = 'ifany')
table(df_sub$DV_alc, useNA = 'ifany') # n = 2196 excluded due to prior initiation


table(df_sub$DV_cb_30m, useNA = 'ifany')
table(df_sub$DV_cb_3y, useNA = 'ifany')
table(df_sub$DV_cb, useNA = 'ifany') # n = 85 excluded due to prior initiation

# convert final DV variables to 2-category and merge with final dataset

df_sub <- df_sub %>% 
  mutate(
    DV_alc = case_when(
      DV_alc == 'Excluded due to prior initiation' ~ NA,
      DV_alc == 'Yes' ~ 1,
      DV_alc == 'No' ~ 0),
    DV_cb = case_when(
      DV_cb == 'Excluded due to prior initiation' ~ NA,
      DV_cb == 'Yes' ~ 1,
      DV_cb == 'No' ~ 0),
    DV_alc = as.numeric(DV_alc),
    DV_cb = as.numeric(DV_cb)) %>% 
  select(src_subject_id, DV_alc, DV_cb)

table(df_sub$DV_alc, useNA = 'ifany')
table(df_sub$DV_cb, useNA = 'ifany')

DV_alc_table <- table(df_sub$DV_alc, useNA = 'ifany')
capture.output(DV_alc_table, file = 'output/DV_alc_table.txt')

DV_cb_table <- table(df_sub$DV_cb, useNA = 'ifany')
capture.output(DV_cb_table, file = 'output/DV_cb_table.txt')

df_final <- df_final %>% 
  left_join(df_sub, by = 'src_subject_id')

write.csv(df_sub, 'output/df_sub.csv')

rm(df_sub, su_mid, su_yr, su_mid_wide, su_yr_wide)

write.csv(df_final, 'output/df_final.csv')

#------------------------------------------------------------------------------#
#           Expectancy Questionnaires: Alcohol and Cannabis
#------------------------------------------------------------------------------#

# Note: must have complete data for individual items for summary score

su_y_alc_exp <- read_csv('data/su_y_alc_exp.csv') %>%
  subset(eventname == '2_year_follow_up_y_arm_1') %>%
  select(src_subject_id, aeq_positive_expectancies_ss) %>%
  rename(
    alc_exp = aeq_positive_expectancies_ss) %>%
  select(src_subject_id, alc_exp)
  
su_y_can_exp <- read_csv('data/su_y_can_exp.csv') %>%
  subset(eventname == '2_year_follow_up_y_arm_1') %>%
  select(src_subject_id, meeq_positive_expectancies_ss) %>%
  rename(
    cb_exp = meeq_positive_expectancies_ss) %>%
  select(src_subject_id, cb_exp)

# merge w/final dataset
df_final <- df_final %>%
  left_join(su_y_alc_exp, by = 'src_subject_id') %>%
  left_join(su_y_can_exp, by = 'src_subject_id')
rm(su_y_alc_exp, su_y_can_exp)

#------------------------------------------------------------------------------#
#             Perception of Harm Questionnaires: Alcohol and Cannabis
#------------------------------------------------------------------------------#
# Note: must have complete data for individual items for summary score

su_y_percharm <- read_csv('data/su_y_percharm.csv') %>%
  subset(eventname == '2_year_follow_up_y_arm_1') %>%
  right_join(df_final_ID, by = 'src_subject_id') %>% 
  select(src_subject_id, phs_1_y, phs_2_y, phs_3_y, phs_9_y, phs_10_y, phs_11_y) 

#--- RG Note: 
# breakdown of number that indicated (999) = 'Don't Know' to recode to NA
table(su_y_percharm$phs_1_y, useNA = 'ifany') 
table(su_y_percharm$phs_2_y, useNA = 'ifany') 
table(su_y_percharm$phs_3_y, useNA = 'ifany') 
table(su_y_percharm$phs_9_y, useNA = 'ifany') 
table(su_y_percharm$phs_10_y, useNA = 'ifany') 
table(su_y_percharm$phs_11_y, useNA = 'ifany') 
#--- RG Note: 

# recode (999) to NA
su_y_percharm <- su_y_percharm %>% 
    mutate(
    phs_1_y = ifelse(phs_1_y == 999, NA, phs_1_y),
    phs_2_y = ifelse(phs_2_y == 999, NA, phs_2_y),
    phs_3_y = ifelse(phs_3_y == 999, NA, phs_3_y),
    phs_9_y = ifelse(phs_9_y == 999, NA, phs_9_y),
    phs_10_y = ifelse(phs_10_y == 999, NA, phs_10_y),
    phs_11_y = ifelse(phs_11_y == 999, NA, phs_11_y)) %>% 
  mutate(
    alc_per = rowSums(select(., c(phs_1_y, phs_2_y, phs_3_y)), na.rm = TRUE),
    cb_per = rowSums(select(., c(phs_9_y, phs_10_y, phs_11_y)), na.rm = TRUE)) 

#--- RG Note:
# - summary scores (alc_per & cb_per): na.rm = TRUE indicates that summary 
#   scores will be created ignoring values of NA (i.e., if an ID has data 
#   present for only 1 item, summary score will reflect that 1 item and ignore
#   missing data for other 2 items)
# - breakdown of participants w/1, 2, or all 3 individual items complete
su_y_percharm <- su_y_percharm %>% 
  mutate(
    alc_per_count = case_when(
      is.na(phs_1_y) & is.na(phs_2_y) & is.na(phs_3_y) ~ 'Missing 3 items',
      
      is.na(phs_1_y) & is.na(phs_2_y) & !is.na(phs_3_y) ~ 'Missing 2 items',
      is.na(phs_1_y) & !is.na(phs_2_y) & is.na(phs_3_y) ~ 'Missing 2 items',
      !is.na(phs_1_y) & is.na(phs_2_y) & is.na(phs_3_y) ~ 'Missing 2 items',
      
      is.na(phs_1_y) & !is.na(phs_2_y) & !is.na(phs_3_y) ~ 'Missing 1 item',
      !is.na(phs_1_y) & is.na(phs_2_y) & !is.na(phs_3_y) ~ 'Missing 1 item',
      !is.na(phs_1_y) & !is.na(phs_2_y) & is.na(phs_3_y) ~ 'Missing 1 item',
      
      !is.na(phs_1_y) & !is.na(phs_2_y) & !is.na(phs_3_y) ~ 'Missing 0 items'),
    
    cb_per_count = case_when(
      is.na(phs_9_y) & is.na(phs_10_y) & is.na(phs_11_y) ~ 'Missing 3 items',
      
      is.na(phs_9_y) & is.na(phs_10_y) & !is.na(phs_11_y) ~ 'Missing 2 items',
      is.na(phs_9_y) & !is.na(phs_10_y) & is.na(phs_11_y) ~ 'Missing 2 items',
      !is.na(phs_9_y) & is.na(phs_10_y) & is.na(phs_11_y) ~ 'Missing 2 items',
      
      is.na(phs_9_y) & !is.na(phs_10_y) & !is.na(phs_11_y) ~ 'Missing 1 item',
      !is.na(phs_9_y) & is.na(phs_10_y) & !is.na(phs_11_y) ~ 'Missing 1 item',
      !is.na(phs_9_y) & !is.na(phs_10_y) & is.na(phs_11_y) ~ 'Missing 1 item',
      
      !is.na(phs_9_y) & !is.na(phs_10_y) & !is.na(phs_11_y) ~ 'Missing 0 items'))

table(su_y_percharm$alc_per_count, useNA = 'ifany')
# Missing 0 items  Missing 1 item Missing 2 items Missing 3 items 
#            8222             344              69              78 

harm_alc_count <- table(su_y_percharm$alc_per_count, useNA = 'ifany')
capture.output(harm_alc_count, file = 'output/harm_alc_count.txt')

table(su_y_percharm$cb_per_count, useNA = 'ifany')
# Missing 0 items  Missing 1 item Missing 2 items Missing 3 items 
#            7757             171              55             730 

harm_cb_count <- table(su_y_percharm$cb_per_count, useNA = 'ifany')
capture.output(harm_cb_count, file = 'output/harm_cb_count.txt')

# confirm currently no missing data for either summary score
describe(su_y_percharm$alc_per) # (NA) = 0
describe(su_y_percharm$cb_per) # (NA) = 0

# update summary score: if missing all 3 items, change summary score of 0 to NA
su_y_percharm <- su_y_percharm %>% 
  mutate(
    alc_per = ifelse(alc_per_count == 'Missing 3 items', NA, alc_per),
    cb_per = ifelse(cb_per_count == 'Missing 3 items', NA, cb_per))

# confirm missing data present fpr those who were missing all 3 items
describe(su_y_percharm$alc_per) # (NA) = 78
describe(su_y_percharm$cb_per) # (NA) = 730

#--- RG Note:

# merge w/final dataset
su_y_percharm <- su_y_percharm %>% 
  select(src_subject_id, alc_per, cb_per)

df_final <- df_final %>%
  left_join(su_y_percharm, by = 'src_subject_id')

rm(su_y_percharm)

#------------------------------------------------------------------------------#
#           Longitudinal Tracking: Baseline Age, Site ID, Family ID
#------------------------------------------------------------------------------#

abcd_y_lt <- read_csv('data/abcd_y_lt.csv') %>%
  subset(eventname == 'baseline_year_1_arm_1') %>%
  mutate(age_baseline = interview_age/12) %>% # convert age in months to years
  select(src_subject_id, age_baseline, site_id_l, rel_family_id)
abcd_y_lt$age_baseline <- round(abcd_y_lt$age_baseline, digits = 0)

# merge w/final dataset
df_final <- df_final %>%
  left_join(abcd_y_lt, by = 'src_subject_id')

rm(abcd_y_lt)
  
#------------------------------------------------------------------------------#
#                       Parent Demographics Survey 
#------------------------------------------------------------------------------#

abcd_p_demo <- read_csv('data/abcd_p_demo.csv') %>%
  subset (eventname == 'baseline_year_1_arm_1') %>%
  right_join(df_final_ID, by = 'src_subject_id') %>% 
  select(src_subject_id, demo_sex_v2, demo_comb_income_v2,
         demo_race_a_p___10:demo_race_a_p___25, demo_race_a_p___0,
         demo_race_a_p___77, demo_race_a_p___99,
         demo_ethn_v2) %>%
  mutate(
    sex = factor(demo_sex_v2,
                 levels = c(1,2,3,4),
                 labels = c('Male', 'Female',
                            'Intersex-Male', 'Intersex-Female')),
    eth_hisp = factor(demo_ethn_v2,
                      levels = c(1,2),
                      labels = c('Hispanic', 'non-Hispanic')),
    income = factor(demo_comb_income_v2,
                    levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
                    labels = c('inc_1', 'inc_2', 'inc_3', 'inc_4', 'inc_5',
                               'inc_6', 'inc_7', 'inc_8', 'inc_9', 'inc_10')))
table(abcd_p_demo$sex)
table(abcd_p_demo$eth_hisp)
table(abcd_p_demo$income)

levels(abcd_p_demo$sex)
levels(abcd_p_demo$eth_hisp)
levels(abcd_p_demo$income)

#--- RG Note:
# for variables recoded, number of (777) or (999)
table(abcd_p_demo$demo_sex_v2, useNA = 'ifany') 
table(abcd_p_demo$demo_comb_income_v2, useNA = 'ifany') 
table(abcd_p_demo$demo_ethn_v2, useNA = 'ifany')
#--- RG Note:

# recode values of (777) Refuse to Answer and (999) as NA
abcd_p_demo <- abcd_p_demo %>%
  mutate(
    across(.cols = ends_with('_v2'),
           .fns = ~replace(.x, .x %in% c(999, 777), NA)))

# create summary race variables
abcd_p_demo <- abcd_p_demo %>%
  mutate(
    White = ifelse(demo_race_a_p___10 == 1, 1, 0),
    Black = ifelse(demo_race_a_p___11 == 1, 1, 0),
    Asian = ifelse(demo_race_a_p___18 == 1 | demo_race_a_p___19 == 1 |
                     demo_race_a_p___20 == 1 | demo_race_a_p___21 == 1 |
                     demo_race_a_p___22 == 1 | demo_race_a_p___23 == 1 |
                     demo_race_a_p___24 == 1, 1, 0),
    AIAN = ifelse( #AIAN: American Indian Alaskan Native
      demo_race_a_p___12 == 1 | demo_race_a_p___13 == 1, 1, 0),
    NHPI = ifelse( #NHPI: Native Hawaiian and Other Pacific
      demo_race_a_p___14 == 1 | demo_race_a_p___15 == 1 |
        demo_race_a_p___16 == 1 | demo_race_a_p___17, 1, 0),
    Other = ifelse(demo_race_a_p___25 == 1 | demo_race_a_p___0 == 1, 1, 0)) %>%
  mutate(
    MultiRacial = ifelse(
      (White + Black + Asian + AIAN + NHPI + Other) > 1, 1, 0)) %>%
  mutate(
    race_4l = case_when(
      White == 1 & (Black == 0 & Asian == 0 & AIAN == 0 & NHPI == 0 & Other == 0
                    & MultiRacial == 0) ~ 'White', 
      Black == 1 & (White == 0 & Asian == 0 & AIAN == 0 & NHPI == 0 & Other == 0
                    & MultiRacial == 0) ~ 'Black',
      Asian == 1 & (White == 0 & Black == 0 & AIAN == 0 & NHPI == 0 & Other == 0
                    & MultiRacial == 0) ~ 'Asian',
      AIAN == 1 | NHPI == 1 | Other == 1 | MultiRacial == 1 ~
        'Other/MultiRacial'),
    race_4l = factor(race_4l))

# subset relevant variables
abcd_p_demo <- abcd_p_demo %>%
  select(src_subject_id, sex, race_4l, eth_hisp, income)

# re-code 2IDs from intersex male to male
table(abcd_p_demo$sex, useNA = 'ifany')

abcd_p_demo <- abcd_p_demo %>%
  mutate(
    sex = case_when(
    sex == 'Intersex-Male' ~ 'Male',
    sex == 'Male' ~ 'Male',
    sex == 'Female' ~ 'Female')) %>%
  mutate(sex = as.factor(sex))
  
# merge w/final dataset 
df_final <- df_final %>%
  left_join(abcd_p_demo, by = 'src_subject_id')
rm(abcd_p_demo)

# age
concordance_age <- read_csv('data/su_y_sui.csv') %>%
  subset(eventname == '2_year_follow_up_y_arm_1') %>%
  select(src_subject_id, tlfb_age_l, tlfb_age_calc_inmonths_l)

# merge w/final dataset 
df_final <- df_final %>%
  left_join(concordance_age, by = 'src_subject_id')
rm(concordance_age)

#------------------------------------------------------------------------------#
#                    Developmental History Questionnaire                       #
#------------------------------------------------------------------------------#

ph_p_dhx <- read_csv('data/ph_p_dhx.csv') %>%
  subset (eventname == 'baseline_year_1_arm_1') %>%
  right_join(df_final_ID, by = 'src_subject_id') %>% 
  select(src_subject_id,
         devhx_8_alcohol, devhx_8_tobacco, devhx_8_marijuana,
         devhx_8_coc_crack, devhx_8_her_morph, devhx_8_oxycont,
         devhx_8_other_drugs,
         devhx_9_alcohol, devhx_9_tobacco, devhx_9_marijuana,
         devhx_9_coc_crack, devhx_9_her_morph, devhx_9_oxycont,
         devhx_9_other_drugs)

#--- RG NOTE: 
# - breakdown of values to be recoded
table(ph_p_dhx$devhx_8_alcohol, useNA = 'ifany') 
table(ph_p_dhx$devhx_8_tobacco, useNA = 'ifany') 
table(ph_p_dhx$devhx_8_marijuana, useNA = 'ifany') 
table(ph_p_dhx$devhx_8_coc_crack, useNA = 'ifany') 
table(ph_p_dhx$devhx_8_her_morph, useNA = 'ifany') 
table(ph_p_dhx$devhx_8_oxycont, useNA = 'ifany') 
table(ph_p_dhx$devhx_8_other_drugs, useNA = 'ifany') 

table(ph_p_dhx$devhx_9_alcohol, useNA = 'ifany') 
table(ph_p_dhx$devhx_9_tobacco, useNA = 'ifany') 
table(ph_p_dhx$devhx_9_marijuana, useNA = 'ifany')
table(ph_p_dhx$devhx_9_coc_crack, useNA = 'ifany') 
table(ph_p_dhx$devhx_9_her_morph, useNA = 'ifany') 
table(ph_p_dhx$devhx_9_oxycont, useNA = 'ifany') 
table(ph_p_dhx$devhx_9_other_drugs, useNA = 'ifany') 
#--- RG NOTE: 

# re-code values of 999 to NA
ph_p_dhx <- ph_p_dhx %>%
  mutate(
    across(.cols = starts_with('devhx_8') | starts_with('devhx_9'),
           .fns = ~replace(.x, .x %in% c(999), NA)))

# count NA across all vars
ph_p_dhx$count_na_dhx <- rowSums(is.na(select(ph_p_dhx, 
                                              starts_with('devhx_8') |
                                                starts_with('devhx_9'))))

# create binary substance exposure variable
# note: if missing data on all 14 variables, coded as NA otherwise using data
# present to create exposure variable
ph_p_dhx <- ph_p_dhx %>%
  mutate(exp_sub = rowSums((select(
    ph_p_dhx, starts_with('devhx_8') | starts_with('devhx_9'))),
    na.rm = TRUE),
    exp_sub = ifelse(exp_sub == 0, 0, 1),
    exp_sub = ifelse(count_na_dhx == 14, NA, exp_sub),
    exp_sub = factor(exp_sub,
                     levels = c(0, 1),
                     labels = c('No', 'Yes')))

# subset to relevant variables
ph_p_dhx <- ph_p_dhx %>%
  select(src_subject_id, exp_sub)

# merge w/final dataset
df_final <- df_final %>%
  left_join(ph_p_dhx, by = 'src_subject_id')
rm(ph_p_dhx)

#------------------------------------------------------------------------------#
#                     Family History Questionnaire 
#------------------------------------------------------------------------------#
mh_p_fhx <- read_csv('data/mh_p_fhx.csv') %>%
  subset (eventname == 'baseline_year_1_arm_1') %>%
  right_join(df_final_ID, by = 'src_subject_id') %>% 
  select(src_subject_id,
         famhx_ss_fath_prob_alc_p, famhx_ss_patgf_prob_alc_p,
         famhx_ss_patgm_prob_alc_p, famhx_ss_moth_prob_alc_p,
         famhx_ss_matgf_prob_alc_p, famhx_ss_matgm_prob_alc_p,
         famhx_ss_fath_prob_dg_p, famhx_ss_patgf_prob_dg_p,
         famhx_ss_patgm_prob_dg_p, famhx_ss_moth_prob_dg_p,
         famhx_ss_matgf_prob_dg_p, famhx_ss_matgm_prob_dg_p)

# create values for each family member
mh_p_fhx<- mh_p_fhx %>%
  mutate(
    across(.cols = starts_with('famhx_ss_moth_prob') |
             starts_with('famhx_ss_fath_prob'),
           .fns = ~replace(.x, .x == 1, .50))) %>%
  mutate(
    across(.cols = starts_with('famhx_ss_matg') |
             starts_with('famhx_ss_patg'),
           .fns = ~replace(.x, .x == 1, .25)))

# count number missing
mh_p_fhx$count_na_fhx <- rowSums(is.na(select(mh_p_fhx, starts_with('famhx'))))

# create density score
mh_p_fhx$mh_density <- rowSums(
  (select(mh_p_fhx, starts_with('famhx'))), na.rm = TRUE)

# if missing all variables used in density score, code as NA
mh_p_fhx <- mh_p_fhx %>%
  mutate(mh_density = ifelse(count_na_fhx == 12, NA, mh_density))

# subset to relevant variables
mh_p_fhx <- mh_p_fhx %>%
  select(src_subject_id, mh_density)

# merge w/final dataset
df_final <- df_final %>%
  left_join(mh_p_fhx, by = 'src_subject_id')
rm(mh_p_fhx)

#------------------------------------------------------------------------------#
#               Child Behavior Checklist Scores (CBCL)
#------------------------------------------------------------------------------#

mh_p_cbcl<- read_csv('data/mh_p_cbcl.csv') %>%
  subset (eventname == 'baseline_year_1_arm_1') %>%
  select(src_subject_id, cbcl_scr_syn_totprob_r, cbcl_scr_syn_internal_r, 
         cbcl_scr_syn_external_r)

# merge w/final dataset
df_final <- df_final %>%
  left_join(mh_p_cbcl, by = 'src_subject_id')
rm(mh_p_cbcl)

#------------------------------------------------------------------------------#
#                           Finalize Datasets
#------------------------------------------------------------------------------#

# check breakdown of outcomes for each model
describe(df_final$DV_alc) # n = 6517
describe(df_final$DV_cb) # n = 8628
describe(df_final$alc_exp) # n = 8709
describe(df_final$cb_exp) # n = 8159
describe(df_final$alc_per) # n = 8635
describe(df_final$cb_per) # n = 7893
#--- RG NOTE:
# - updated n above based on RG updates
#--- RG NOTE:

# check variable type
str(df_final)

# breakdown of missing data
obs_NA_factor <- df_final %>%
  select_if(~ any(is.na(.))) %>%
  select_if( ~ is.factor(.))

obs_NA_numeric <- df_final %>%
  select_if(~ any(is.na(.))) %>%
  select_if(~is.numeric(.))

obs_NA_factor <- obs_NA_factor %>%
  Desc(., plotit = FALSE)
capture.output(obs_NA_factor, file = 'output/obs_NA_factor.txt')

obs_NA_numeric <- obs_NA_numeric %>%
  Desc(., plotit = FALSE)
capture.output(obs_NA_numeric, file = 'output/obs_NA_numeric.txt')

rm(obs_NA_factor, obs_NA_numeric)

# check sample sizes for complete cases
#--- RG NOTE:
# - subset dataset to only include predictors, covariates, and outcomes
df_final_sub <- df_final %>% 
  select(
    # outcome
    DV_alc, DV_cb, alc_exp, cb_exp, alc_per, cb_per, 
    # predictors
    cc_cb, cc_alc,
    # covariates
    tlfb_age_l, sex, race_4l, eth_hisp, income, exp_sub, mh_density, 
    cbcl_scr_syn_external_r, cbcl_scr_syn_internal_r)
#--- RG NOTE:

df_final_cc <- df_final_sub[complete.cases(df_final_sub), ] # n = 4206

write.csv(df_final_cc, 'output/df_final_cc.csv')
write.csv(df_final_sub, 'output/df_final_sub.csv')

rm(df_final_cc, df_final_sub)

```


## MICE


```{r eval = FALSE}
#------------------------------------------------------------------------------#
#                     Multiple Imputation: MICE
#------------------------------------------------------------------------------#

## Configure parallelization
## Detect core count
nCores <- min(parallel::detectCores())

#--- RG NOTE:
# - previous syntax below
# nCores <- min(parallel::detectCores(), 8)
# - minor update to not set cores to 8, but allow more or less cores to be
#   used depending on computer
#--- RG NOTE:

## Used by parallel::mclapply() as default
options(mc.cores = nCores)

## Used by doParallel as default
options(cores = nCores)

## Register doParallel as the parallel backend with foreach
doParallel::registerDoParallel(cores = nCores)

## Report multicore use
cat("### Using", foreach::getDoParWorkers(), "cores\n")
cat("### Using", foreach::getDoParName(), "as backend\n")
cat("
    ###
    ### Missing data imputation with mice
    ########################################################################\n")

## Create a before-MI dataset
df_final_before <- df_final

## Extract all variable names in dataset
allVars <- names(df_final_before)

## names of variables with missingness
missVars <- names(df_final_before)[colSums(is.na(df_final_before)) > 0]

## mice predictorMatrix
predictorMatrix <- matrix(0, ncol = length(allVars),
                          nrow = length(allVars))
rownames(predictorMatrix) <- allVars
colnames(predictorMatrix) <- allVars

## Avoid perfect linear dependence
cat("
    ### Specify Variables informing imputation\n")

## These can be either complete variables or variables with missingness.
## Those with missingness must be imputed.
## Explicitly specify.
imputerVars <- c('age_baseline', 'sex', 'race_4l', 'eth_hisp', 'income')

## Keep variables that actually exist in dataset
imputerVars <- intersect(unique(imputerVars), allVars)
imputerVars
imputerMatrix <- predictorMatrix
imputerMatrix[,imputerVars] <- 1
imputerMatrix
cat("
    ### Specify variables with missingness to be imputed \n")

imputedOnlyVars <- c(
  'tlfb_age_l', 'race_4l', 'eth_hisp', 'income', 'exp_sub', 'mh_density', 
  'cbcl_scr_syn_totprob_r', 'cbcl_scr_syn_internal_r', 
  'cbcl_scr_syn_external_r')

## imputers that have missingness must be imputed.
imputedVars <- intersect(unique(c(imputedOnlyVars, imputerVars)), missVars)
imputedVars
imputedMatrix <- predictorMatrix
imputedMatrix[imputedVars,] <- 1
imputedMatrix

cat("
    ### Construct a full predictor matrix
    ### (rows: imputed variables; cols: imputer variables)\n")

## keep correct imputer-imputed pairs only
predictorMatrix <- imputerMatrix * imputedMatrix
## diagonals must be zeros (a variable cannot impute itself)
diag(predictorMatrix) <- 0
predictorMatrix

cat("
### Dry-run mice for imputation methods\n")
dryMice <- mice(data = df_final_before, m = 1,
                predictorMatrix = predictorMatrix, maxit = 0)

## update predictor matrix
predictorMatrix <- dryMice$predictorMatrix
cat("### Imputers (non-zero columns of predictorMatrix)\n")
imputerVars <- colnames(predictorMatrix)[colSums(predictorMatrix) > 0]
imputerVars
cat("### Imputed (non-zero rows of predictorMatrix)\n")
imputedVars <- rownames(predictorMatrix)[rowSums(predictorMatrix) > 0]
imputedVars
cat("### Imputers that are complete\n")
setdiff(imputerVars, imputedVars)
cat("### Imputers with missingness\n")
intersect(imputerVars, imputedVars)
cat("### Imputed-only variables without being imputers\n")
setdiff(imputedVars, imputerVars)
cat("### Variables with missingness that are not imputed\n")
setdiff(missVars, imputedVars)
cat("### Relevant part of predictorMatrix\n")
predictorMatrix[rowSums(predictorMatrix) > 0, colSums(predictorMatrix) > 0]

dryMice$method[setdiff(allVars, imputedVars)] <- ""
cat("### Methods used for imputation\n")
# output methods used for each variable
methods <- dryMice$method[sapply(dryMice$method, nchar) > 0]
capture.output(methods, file = 'output/methods.txt')

cat("
    ### Run mice\n")
M <- 5
cat("### Imputing", M, "times\n")
## set seed for reproducibility
set.seed(29403)

## parallelized execution
miceout <- foreach(i = seq_len(M), .combine = ibind) %dorng% {
  cat("### Started iteration", i, "\n")
  miceout <- mice::mice(
    data = df_final_before, m = 1,
    print = TRUE, predictorMatrix = predictorMatrix,
    method = dryMice$method, maxit = 20)
  cat("### Completed iteration", i, "\n")
  ## Make sure to return the output
  miceout
}

logged_events <- miceout$loggedEvents
logged_events # NULL
rm(logged_events)

cat("
    ### Show mice results\n")
## mice object ifself
miceout
## variables that no longer have missingness after imputation
cat("
    ### Variables actually imputed\n")
actuallyImputedVars <-
  setdiff(names(df_final_before)[colSums(is.na(df_final_before)) > 0],
          names(mice::complete(miceout, action = 1))
          [colSums(is.na(mice::complete(miceout, action = 1))) > 0])
actuallyImputedVars
## examine discrepancies
cat("### Variables that were unexpectedly imputed\n")
setdiff(actuallyImputedVars, imputedVars)
cat("### Variables that were planned for MI but not imputed\n")
setdiff(imputedVars, actuallyImputedVars)
```


## Prep final dataset for models


```{r eval = FALSE}

#--- RG NOTE:
# - packages for mixed models will only use data available, so you don't have 
#   to create separate mids objects for each outcome 

# convert mids object into dataframe
mice_df_final <-mice::complete(miceout, "long", include = TRUE)
table(mice_df_final$.imp)
 
mice_df_final$cc_alc <- relevel(mice_df_final$cc_alc, 
                                ref = 'Concordance Limited A')
mice_df_final$cc_cb <-relevel(mice_df_final$cc_cb, 
                              ref = 'Concordance Limited C')

mice_df_final$sex <- relevel(mice_df_final$sex, ref = 'Male')
mice_df_final$race_4l <- relevel(mice_df_final$race_4l, ref = 'White')
mice_df_final$eth_hisp <- relevel(mice_df_final$eth_hisp, ref = 'non-Hispanic')
mice_df_final$income <- relevel(mice_df_final$income, ref = 'inc_9')
mice_df_final$exp_sub <- relevel(mice_df_final$exp_sub, ref = 'No')

# save as mids object
mids_df_final <- as.mids(mice_df_final)

write.csv(mice_df_final, 'output/mice_df_final.csv')
write.csv(df_final_before, 'output/df_final_before.csv')

rm(
   actuallyImputedVars, allVars, imputedOnlyVars, imputedVars, imputerVars,
   M, methods, missVars, predictorMatrix, imputedMatrix, imputerMatrix, dryMice)

#--- RG NOTE:

# CM original syntax below 

# # convert mids object into dataframe
# mice_df_final <-mice::complete(miceout, "long", include = TRUE)
# table(mice_df_final$.imp)
# 
# # alcohol initiation:
# # - complete data on alcohol initiation
# mice_df_alc <- mice_df_final %>%
#   subset(!is.na(DV_alc))
# table(mice_df_alc$DV_alc, useNA = 'ifany')
# table(mice_df_alc$.imp, useNA = 'ifany')
# 
# # cannabis initiation:
# # - complete data on alcohol initiation
# mice_df_cb <- mice_df_final %>%
#   subset(!is.na(DV_cb))
# table(mice_df_cb$DV_cb, useNA = 'ifany')
# table(mice_df_cb$.imp, useNA = 'ifany')
# 
# # set reference group
# mice_df_alc$cc_alc <- relevel(factor(mice_df_alc$cc_alc), ref = 'Concordance Limited A')
# mice_df_final$cc_alc <- relevel(factor(mice_df_final$cc_alc), ref = 'Concordance Limited A')
# 
# mice_df_cb$cc_cb <-relevel(factor(mice_df_cb$cc_cb), ref = 'Concordance Limited C')
# mice_df_final$cc_cb <-relevel(factor(mice_df_final$cc_cb), ref = 'Concordance Limited C')
# 
# mice_df_alc$sex <- relevel(mice_df_alc$sex, ref = 'Male')
# mice_df_cb$sex <- relevel(mice_df_cb$sex, ref = 'Male')
# mice_df_final$sex <- relevel(mice_df_final$sex, ref = 'Male')
# 
# mice_df_alc$race_4l <- relevel(mice_df_alc$race_4l, ref = 'White')
# mice_df_cb$race_4l <- relevel(mice_df_cb$race_4l, ref = 'White')
# mice_df_final$race_4l <- relevel(mice_df_final$race_4l, ref = 'White')
# 
# mice_df_alc$eth_hisp <- relevel(mice_df_alc$eth_hisp, ref = 'non-Hispanic')
# mice_df_cb$eth_hisp <- relevel(mice_df_cb$eth_hisp, ref = 'non-Hispanic')
# mice_df_final$eth_hisp <- relevel(mice_df_final$eth_hisp, ref = 'non-Hispanic')
# 
# mice_df_alc$income <- relevel(mice_df_alc$income, ref = 'inc_9')
# mice_df_cb$income <- relevel(mice_df_cb$income, ref = 'inc_9')
# mice_df_final$income <- relevel(mice_df_final$income, ref = 'inc_9')
# 
# mice_df_alc$exp_sub <- relevel(mice_df_alc$exp_sub, ref = 'No')
# mice_df_cb$exp_sub <- relevel(mice_df_cb$exp_sub, ref = 'No')
# mice_df_final$exp_sub <- relevel(mice_df_final$exp_sub, ref = 'No')
# 
# # save as mids object
# mids_alc <- as.mids(mice_df_alc)
# mids_cb <- as.mids(mice_df_cb)
# mids_df_final <- as.mids(mice_df_final)
# 
# rm(mice_df_alc, mice_df_cb, mice_df_final,
#    actuallyImputedVars, allVars, imputedOnlyVars, imputedVars, imputerVars,
#    M, methods, missVars, predictorMatrix, imputedMatrix, imputerMatrix, dryMice,
#    df_final_before)

```


# Sample Characteristics


```{r eval = FALSE}

# items for figure
# - mean and SD of expectancies questionnaire in each group

# outcome: expectancies

fig_alc_exp <- df_final %>%
  group_by(cc_alc) %>%
  select(cc_alc, alc_exp) %>%
  summarise(
    alc_exp_mean = mean(alc_exp, na.rm = TRUE),
    alc_exp_sd = sd(alc_exp, na.rm = TRUE),
    alc_exp_min = min(alc_exp, na.rm = TRUE),
    alc_exp_max = max(alc_exp, na.rm = TRUE))

write.csv(fig_alc_exp,'output/fig_alc_exp.csv')
rm(fig_alc_exp)

fig_cb_exp <- df_final %>%
  group_by(cc_cb) %>%
  select(cc_cb, cb_exp) %>%
  summarise(
    cb_exp_mean = mean(cb_exp, na.rm = TRUE),
    cb_exp_sd = sd(cb_exp, na.rm = TRUE),
    cb_exp_min = min(cb_exp, na.rm = TRUE),
    cb_exp_max = max(cb_exp, na.rm = TRUE))

write.csv(fig_cb_exp,'output/fig_cb_exp.csv')
rm(fig_cb_exp)

# outcome: perception

fig_alc_perc <- df_final %>%
  group_by(cc_alc) %>%
  select(cc_alc, alc_per) %>%
  summarise(
    alc_per_mean = mean(alc_per, na.rm = TRUE),
    alc_per_sd = sd(alc_per, na.rm = TRUE),
    alc_per_min = min(alc_per, na.rm = TRUE),
    alc_per_max = max(alc_per, na.rm = TRUE))

write.csv(fig_alc_perc,'output/fig_alc_perc.csv')
rm(fig_alc_perc)

fig_cb_perc <- df_final %>%
  group_by(cc_cb) %>%
  select(cc_cb, cb_per) %>%
  summarise(
    cb_per_mean = mean(cb_per, na.rm = TRUE),
    cb_per_sd = sd(cb_per, na.rm = TRUE),
    cb_per_min = min(cb_per, na.rm = TRUE),
    cb_per_max = max(cb_per, na.rm = TRUE))

write.csv(fig_cb_perc,'output/fig_cb_perc.csv')
rm(fig_cb_perc)

# outcome: initiation
DV_alc_freq <- table(df_final$DV_alc, useNA = 'ifany')
DV_alc_prop <- prop.table(table(df_final$DV_alc, useNA = 'ifany'))
DV_alc <- cbind(DV_alc_freq, DV_alc_prop)
capture.output(DV_alc, file = 'output/DV_alc.txt')
rm(DV_alc_freq, DV_alc_prop, DV_alc)

DV_cb_freq <- table(df_final$DV_cb, useNA = 'ifany')
DV_cb_prop <- prop.table(table(df_final$DV_cb, useNA = 'ifany'))
DV_cb <- cbind(DV_cb_freq, DV_cb_prop)
capture.output(DV_cb, file = 'output/DV_cb.txt')
rm(DV_cb_freq, DV_cb_prop, DV_cb)

# factor substance use
obs_factor_alc <- df_final %>%
  gather(variable, value, cc_alc) %>%
  group_by(variable, value) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n) * 100) %>%
  mutate(freq = round(freq, digits = 2))
write.csv(obs_factor_alc,'output/obs_factor_alc.csv')
rm(obs_factor_alc)

obs_factor_cb <- df_final %>%
  gather(variable, value, cc_cb) %>%
  group_by(variable, value) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n) * 100) %>%
  mutate(freq = round(freq, digits = 2))
write.csv(obs_factor_cb,'output/obs_factor_cb.csv')
rm(obs_factor_cb)

# - proportion of SU initiation within each group
fig_alcYN_freq <- table(
  df_final$cc_alc, df_final$DV_alc, useNA = 'ifany')
fig_alcYN_prop <- prop.table(table(
  df_final$cc_alc, df_final$DV_alc, useNA = 'ifany'))
capture.output(fig_alcYN_freq, file = 'output/fig_alcYN_freq.txt')
capture.output(fig_alcYN_prop, file = 'output/fig_alcYN_prop.txt')
rm(fig_alcYN_freq, fig_alcYN_prop)

fig_cbYN_freq <- table(
  df_final$cc_cb, df_final$DV_cb, useNA = 'ifany')
fig_cbYN_prop <- prop.table(table(
  df_final$cc_cb, df_final$DV_cb, useNA = 'ifany'))
capture.output(fig_cbYN_freq, file = 'output/fig_cbYN_freq.txt')
capture.output(fig_cbYN_prop, file = 'output/fig_cbYN_prop.txt')
rm(fig_cbYN_freq, fig_cbYN_prop)

# numeric full sample
obs_num_all <- get_summary_stats(df_final, type = "common") %>%
  select(variable, n, mean, sd, min, max)
write.csv(obs_num_all,'output/obs_num_all.csv')
rm(obs_num_all)

# factor full sample
obs_factor_all <- df_final %>%
  gather(variable, value, sex, race_4l, eth_hisp, income, exp_sub, mh_density, 
         cc_alc, cc_cb) %>%
  group_by(variable, value) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n) * 100) %>%
  mutate(freq = round(freq, digits = 2))
write.csv(obs_factor_all,'output/obs_factor_all.csv')
rm(obs_factor_all)

# - proportion of sex within each group
fig_alc_sex_freq <- table(
  df_final$cc_alc, df_final$sex, useNA = 'ifany')
fig_alc_sex_prop <- prop.table(table(
  df_final$cc_alc, df_final$sex, useNA = 'ifany'))
capture.output(fig_alc_sex_freq, file = 'output/fig_alc_sex_freq.txt')
capture.output(fig_alc_sex_prop, file = 'output/fig_alc_sex_prop.txt')
rm(fig_alc_sex_freq, fig_alc_sex_prop)

fig_cb_sex_freq <- table(
  df_final$cc_cb, df_final$sex, useNA = 'ifany')
fig_cb_sex_prop <- prop.table(table(
  df_final$cc_cb, df_final$sex, useNA = 'ifany'))
capture.output(fig_cb_sex_freq, file = 'output/fig_cb_sex_freq.txt')
capture.output(fig_cb_sex_prop, file = 'output/fig_cb_sex_prop.txt')
rm(fig_cb_sex_freq, fig_cb_sex_prop)

# - proportion of race within each group
fig_alc_race_freq <- table(
  df_final$cc_alc, df_final$race_4l, useNA = 'ifany')
fig_alc_race_prop <- prop.table(table(
  df_final$cc_alc, df_final$race_4l, useNA = 'ifany'))
capture.output(fig_alc_race_freq, file = 'output/fig_alc_race_freq.txt')
capture.output(fig_alc_race_prop, file = 'output/fig_alc_race_prop.txt')
rm(fig_alc_race_freq, fig_alc_race_prop)

fig_cb_race_freq <- table(
  df_final$cc_cb, df_final$race_4l, useNA = 'ifany')
fig_cb_race_prop <- prop.table(table(
  df_final$cc_cb, df_final$race_4l, useNA = 'ifany'))
capture.output(fig_cb_race_freq, file = 'output/fig_cb_race_freq.txt')
capture.output(fig_cb_race_prop, file = 'output/fig_cb_race_prop.txt')
rm(fig_cb_race_freq, fig_cb_race_prop)

# - proportion of ethnicity within each group
fig_alc_ethn_freq <- table(
  df_final$cc_alc, df_final$eth_hisp, useNA = 'ifany')
fig_alc_ethn_prop <- prop.table(table(
  df_final$cc_alc, df_final$eth_hisp, useNA = 'ifany'))
capture.output(fig_alc_ethn_freq, file = 'output/fig_alc_ethn_freq.txt')
capture.output(fig_alc_ethn_prop, file = 'output/fig_alc_ethn_prop.txt')
rm(fig_alc_ethn_freq, fig_alc_ethn_prop)

fig_cb_ethn_freq <- table(
  df_final$cc_cb, df_final$eth_hisp, useNA = 'ifany')
fig_cb_ethn_prop <- prop.table(table(
  df_final$cc_cb, df_final$eth_hisp, useNA = 'ifany'))
capture.output(fig_cb_ethn_freq, file = 'output/fig_cb_ethn_freq.txt')
capture.output(fig_cb_ethn_prop, file = 'output/fig_cb_ethn_prop.txt')
rm(fig_cb_ethn_freq, fig_cb_ethn_prop)

# - proportion of income within each group
fig_alc_income_freq <- table(
  df_final$cc_alc, df_final$income, useNA = 'ifany')
fig_alc_income_prop <- prop.table(table(
  df_final$cc_alc, df_final$income, useNA = 'ifany'))
capture.output(fig_alc_income_freq, file = 'output/fig_alc_income_freq.txt')
capture.output(fig_alc_income_prop, file = 'output/fig_alc_income_prop.txt')
rm(fig_alc_income_freq, fig_alc_income_prop)

fig_cb_income_freq <- table(
  df_final$cc_cb, df_final$income, useNA = 'ifany')
fig_cb_income_prop <- prop.table(table(
  df_final$cc_cb, df_final$income, useNA = 'ifany'))
capture.output(fig_cb_income_freq, file = 'output/fig_cb_income_freq.txt')
capture.output(fig_cb_income_prop, file = 'output/fig_cb_income_prop.txt')
rm(fig_cb_income_freq, fig_cb_income_prop)

# - proportion of prenatal exposure within each group
fig_alc_exp_sub_freq <- table(
  df_final$cc_alc, df_final$exp_sub, useNA = 'ifany')
fig_alc_exp_sub_prop <- prop.table(table(
  df_final$cc_alc, df_final$exp_sub, useNA = 'ifany'))
capture.output(fig_alc_exp_sub_freq, file = 'output/fig_alc_exp_sub_freq.txt')
capture.output(fig_alc_exp_sub_prop, file = 'output/fig_alc_exp_sub_prop.txt')
rm(fig_alc_exp_sub_freq, fig_alc_exp_sub_prop)

fig_cb_exp_sub_freq <- table(
  df_final$cc_cb, df_final$exp_sub, useNA = 'ifany')
fig_cb_exp_sub_prop <- prop.table(table(
  df_final$cc_cb, df_final$exp_sub, useNA = 'ifany'))
capture.output(fig_cb_exp_sub_freq, file = 'output/fig_cb_exp_sub_freq.txt')
capture.output(fig_cb_exp_sub_prop, file = 'output/fig_cb_exp_sub_prop.txt')
rm(fig_cb_exp_sub_freq, fig_cb_exp_sub_prop)

# - mean and SD of age in each group

fig_alc_age <- df_final %>%
  group_by(cc_alc) %>%
  select(cc_alc, tlfb_age_l) %>%
  summarise(
    tlfb_age_l_mean = mean(tlfb_age_l, na.rm = TRUE),
    tlfb_age_l_sd = sd(tlfb_age_l, na.rm = TRUE),
    tlfb_age_l_min = min(tlfb_age_l, na.rm = TRUE),
    tlfb_age_l_max = max(tlfb_age_l, na.rm = TRUE))

write.csv(fig_alc_age,'output/fig_alc_age.csv')
rm(fig_alc_age)

fig_cb_age <- df_final %>%
  group_by(cc_cb) %>%
  select(cc_cb, tlfb_age_l) %>%
  summarise(
    tlfb_age_l_mean = mean(tlfb_age_l, na.rm = TRUE),
    tlfb_age_l_sd = sd(tlfb_age_l, na.rm = TRUE),
    tlfb_age_l_min = min(tlfb_age_l, na.rm = TRUE),
    tlfb_age_l_max = max(tlfb_age_l, na.rm = TRUE))

write.csv(fig_cb_age,'output/fig_cb_age.csv')
rm(fig_cb_age)

# - mean and SD of CBCL total in each group

fig_alc_cbcl <- df_final %>%
  group_by(cc_alc) %>%
  select(cc_alc, cbcl_scr_syn_totprob_r, cbcl_scr_syn_internal_r, cbcl_scr_syn_external_r) %>%
  summarise(
    cbcl_scr_syn_totprob_r_mean = mean(cbcl_scr_syn_totprob_r, na.rm = TRUE),
    cbcl_scr_syn_totprob_r_sd = sd(cbcl_scr_syn_totprob_r, na.rm = TRUE),
    cbcl_scr_syn_totprob_r_min = min(cbcl_scr_syn_totprob_r, na.rm = TRUE),
    cbcl_scr_syn_totprob_r_max = max(cbcl_scr_syn_totprob_r, na.rm = TRUE),
    cbcl_scr_syn_internal_r_mean = mean(cbcl_scr_syn_internal_r, na.rm = TRUE),
    ccbcl_scr_syn_internal_r_sd = sd(cbcl_scr_syn_internal_r, na.rm = TRUE),
    cbcl_scr_syn_internal_r_min = min(cbcl_scr_syn_internal_r, na.rm = TRUE),
    cbcl_scr_syn_internal_r_max = max(cbcl_scr_syn_internal_r, na.rm = TRUE),
    cbcl_scr_syn_external_r_mean = mean(cbcl_scr_syn_external_r, na.rm = TRUE),
    cbcl_scr_syn_external_r_sd = sd(cbcl_scr_syn_external_r, na.rm = TRUE),
    cbcl_scr_syn_external_r_min = min(cbcl_scr_syn_external_r, na.rm = TRUE),
    cbcl_scr_syn_external_r_max = max(cbcl_scr_syn_external_r, na.rm = TRUE))
    
write.csv(fig_alc_cbcl,'output/fig_alc_cbcl.csv')
rm(fig_alc_cbcl)

fig_cb_cbcl <- df_final %>%
  group_by(cc_cb) %>%
  select(cc_cb, cbcl_scr_syn_totprob_r, cbcl_scr_syn_internal_r, cbcl_scr_syn_external_r) %>%
  summarise(
    cbcl_scr_syn_totprob_r_mean = mean(cbcl_scr_syn_totprob_r, na.rm = TRUE),
    cbcl_scr_syn_totprob_r_sd = sd(cbcl_scr_syn_totprob_r, na.rm = TRUE),
    cbcl_scr_syn_totprob_r_min = min(cbcl_scr_syn_totprob_r, na.rm = TRUE),
    cbcl_scr_syn_totprob_r_max = max(cbcl_scr_syn_totprob_r, na.rm = TRUE),
    cbcl_scr_syn_internal_r_mean = mean(cbcl_scr_syn_internal_r, na.rm = TRUE),
    ccbcl_scr_syn_internal_r_sd = sd(cbcl_scr_syn_internal_r, na.rm = TRUE),
    cbcl_scr_syn_internal_r_min = min(cbcl_scr_syn_internal_r, na.rm = TRUE),
    cbcl_scr_syn_internal_r_max = max(cbcl_scr_syn_internal_r, na.rm = TRUE),
    cbcl_scr_syn_external_r_mean = mean(cbcl_scr_syn_external_r, na.rm = TRUE),
    cbcl_scr_syn_external_r_sd = sd(cbcl_scr_syn_external_r, na.rm = TRUE),
    cbcl_scr_syn_external_r_min = min(cbcl_scr_syn_external_r, na.rm = TRUE),
    cbcl_scr_syn_external_r_max = max(cbcl_scr_syn_external_r, na.rm = TRUE))
    
write.csv(fig_cb_cbcl,'output/fig_cb_cbcl.csv')
rm(fig_cb_cbcl)

# - mean and SD of family hx in each group

fig_alc_mh_density <- df_final %>%
  group_by(cc_alc) %>%
  select(cc_alc, mh_density) %>%
  summarise(
    mh_density_mean = mean(mh_density, na.rm = TRUE),
    mh_density_sd = sd(mh_density, na.rm = TRUE),
    mh_density_min = min(mh_density, na.rm = TRUE),
    mh_density_max = max(mh_density, na.rm = TRUE))

write.csv(fig_alc_mh_density,'output/fig_alc_mh_density.csv')
rm(fig_alc_mh_density)

fig_cb_mh_density <- df_final %>%
  group_by(cc_cb) %>%
  select(cc_cb, mh_density) %>%
  summarise(
    mh_density_mean = mean(mh_density, na.rm = TRUE),
    mh_density_sd = sd(mh_density, na.rm = TRUE),
    mh_density_min = min(mh_density, na.rm = TRUE),
    mh_density_max = max(mh_density, na.rm = TRUE))

write.csv(fig_cb_mh_density,'output/fig_cb_mh_density.csv')
rm(fig_cb_mh_density)

```


# Models
+ RG updated mice object for models to be mids_df_final for initiation outcomes
+ Question: why are no random effect included for initiation models?
+ RG notes on model fit:
  + (1a) initiation - alcohol
    + highly skewed outcome (238 vs 6279) likely contributing to binned residuals. Would consider some type of matching 
      ([MatchIt](https://cran.r-project.org/web/packages/MatchIt/vignettes/matching-methods.html)) as an alternative model. 
  + (1b) initiation - cannabis
      + highly skewed outcome (63 vs 8565) likely contributing to binned residuals. Would consider some type of matching 
      ([MatchIt](https://cran.r-project.org/web/packages/MatchIt/vignettes/matching-methods.html)) as an alternative model. 
  + (2a) expectancies - alcohol
    + Posterior predictive check plot indicates some positive skew in outcome. You might try a Poisson or negative binomial 
      regression. I suspect the results will be very similar across models. 
  + (2b) expectancies - cannabis
    + Posterior predictive check plot looks like the outcome may fit a bimodal distribution. You might consider trying some 
      type of model for bimodal outcomes such as [multimode](https://cran.r-project.org/web/packages/multimode/multimode.pdf).
      to see if the results change. 
  + (3a) perceptions of harm - alcohol
    + Some indication of heteroscedasticity in the homogeneity of variance plot, you could add robust SE to account for this
      [robustlmm](https://cran.r-project.org/web/packages/robustlmm/robustlmm.pdf). Linearity of residuals is not showing a great
      fit, so you could see if Poisson or negative binomial may improve fit. Bootstrapping is another option to deal with
      non-normality of residuals. 
  + (3b) perceptions of harm - cannabis
    + Posterior predictive check plot indicates some negative skew in the outcome (which may also be contributing to not the best
      fit with the linearity plot). Same suggestion as for alcohol, you could test Poisson or negative binomial. Bootstrapping is
      also an option for non-normality of residuals. 
+ Note
  + Interpreting the plots from the performance package can be a bit subjective. I found one page that I think is a helpful
    [reference](https://easystats.github.io/performance/articles/check_model.html) for looking at plots from the performance 
    package. There is also 

```{r eval = FALSE}

#------------------------------------------------------------------------------#
#                 Final Models - Alcohol Initiation
#------------------------------------------------------------------------------#
#for internship project will keep as is, but will try MatchThem with random effects for publication

fit_alc_DV <- with(mids_df_final,
                   glm(formula = DV_alc ~ cc_alc +
                         tlfb_age_l + sex + race_4l + eth_hisp + income + exp_sub +
                         mh_density + cbcl_scr_syn_external_r + cbcl_scr_syn_internal_r,
                       family = 'binomial')) #runs

fit_alc_DV_summary <- summary(pool(fit_alc_DV),
                              conf.int = TRUE, exponentiate = TRUE) %>%
  rename(OR = estimate ,
         t.statistic = statistic,
         SE = std.error,
         Lower_CI = `2.5 %`,
         Upper_CI = `97.5 %`) %>%
  mutate_if(is.numeric,
            round,
            digits = 5) %>%
  relocate(term, OR, Lower_CI, Upper_CI, SE, t.statistic, df, p.value)
fit_alc_DV_summary
write.csv(fit_alc_DV_summary,'output/fit_alc_DV_summary.csv')
rm(fit_alc_DV_summary)

# check of model diagnostics with Performance package within each imputation
par(mar=c(1,1,1,1))
fit_alc_DV_imp1 <- fit_alc_DV$analyses[[1]]
fit_alc_DV_imp2 <- fit_alc_DV$analyses[[2]]
fit_alc_DV_imp3 <- fit_alc_DV$analyses[[3]]
fit_alc_DV_imp4 <- fit_alc_DV$analyses[[4]]
fit_alc_DV_imp5 <- fit_alc_DV$analyses[[5]]
testDispersion(fit_alc_DV_imp1)
testDispersion(fit_alc_DV_imp2)
testDispersion(fit_alc_DV_imp3)
testDispersion(fit_alc_DV_imp4)
testDispersion(fit_alc_DV_imp5)


# all non-significant
check_singularity(fit_alc_DV_imp1)
check_singularity(fit_alc_DV_imp2)
check_singularity(fit_alc_DV_imp3)
check_singularity(fit_alc_DV_imp4)
check_singularity(fit_alc_DV_imp5)

# all FALSE
vif(fit_alc_DV_imp1)
vif(fit_alc_DV_imp2)
vif(fit_alc_DV_imp3)
vif(fit_alc_DV_imp4)
vif(fit_alc_DV_imp5)

# all < 2
check_outliers(fit_alc_DV_imp1)
check_outliers(fit_alc_DV_imp2)
check_outliers(fit_alc_DV_imp3)
check_outliers(fit_alc_DV_imp4)
check_outliers(fit_alc_DV_imp5)

# no outliers Error in loadNamespace(j <- i[[1L]], c(lib.loc, .libPaths()), versionCheck = vI[[j]]) : namespace insight 0.19.7 is already loaded, but >= 0.19.8 is required
#check_model(fit_alc_DV_imp1, check = "all")
#check_model(fit_alc_DV_imp2, check = "all")
#check_model(fit_alc_DV_imp3, check = "all")
#check_model(fit_alc_DV_imp4, check = "all")
#check_model(fit_alc_DV_imp5, check = "all")

# some issues with binned residuals
br_imp1 <- binned_residuals(fit_alc_DV_imp1)
br_imp2 <- binned_residuals(fit_alc_DV_imp2)
br_imp3 <- binned_residuals(fit_alc_DV_imp3)
br_imp4 <- binned_residuals(fit_alc_DV_imp4)
br_imp5 <- binned_residuals(fit_alc_DV_imp5)
write.csv(br_imp1,'output/br_imp1.csv')
write.csv(br_imp2,'output/br_imp2.csv')
write.csv(br_imp3,'output/br_imp3.csv')
write.csv(br_imp4,'output/br_imp4.csv')
write.csv(br_imp5,'output/br_imp5.csv')

skew(df_final$DV_alc)
hist(df_final$DV_alc)

# likely due to skew in outcome, zero-inflated or negative binomial model
# may be more appropriate
rm(fit_alc_DV,
   fit_alc_DV_imp1, fit_alc_DV_imp2, fit_alc_DV_imp3, fit_alc_DV_imp4,
   fit_alc_DV_imp5,
   br_imp1, br_imp2, br_imp3, br_imp4, br_imp5)

#------------------------------------------------------------------------------#
#                 Final Models - Expectancies
#------------------------------------------------------------------------------#

# random effect: family ID nested within site ID
fit_alc_exp <- with(
  mids_df_final,
  lmer(formula = alc_exp ~ cc_alc + tlfb_age_l + sex + race_4l +
         eth_hisp + income + exp_sub + mh_density + cbcl_scr_syn_external_r +
         cbcl_scr_syn_internal_r + (1 | site_id_l / rel_family_id)))

# summary(fit_alc_exp)
# nobs = data present for alc_exp
fit_alc_exp_summary <- summary(pool(fit_alc_exp), conf.int = TRUE) %>%
  rename(estimate = estimate ,
         t.statistic = statistic,
         SE = std.error,
         Lower_CI = `2.5 %`,
         Upper_CI = `97.5 %`) %>%
  mutate_if(is.numeric,
            round,
            digits = 5) %>%
  relocate(term, estimate, Lower_CI, Upper_CI, SE, t.statistic, df, p.value)
fit_alc_exp_summary
write.csv(fit_alc_exp_summary,'output/fit_alc_exp_summary.csv')
rm(fit_alc_exp_summary)

# check of model diagnostics with Performance package within each imputation
par(mar=c(1,1,1,1))
fit_alc_exp_imp1 <- fit_alc_exp$analyses[[1]]
fit_alc_exp_imp2 <- fit_alc_exp$analyses[[2]]
fit_alc_exp_imp3 <- fit_alc_exp$analyses[[3]]
fit_alc_exp_imp4 <- fit_alc_exp$analyses[[4]]
fit_alc_exp_imp5 <- fit_alc_exp$analyses[[5]]
testDispersion(fit_alc_exp_imp1)
testDispersion(fit_alc_exp_imp2)
testDispersion(fit_alc_exp_imp3)
testDispersion(fit_alc_exp_imp4)
testDispersion(fit_alc_exp_imp5)

# all non-significant
check_singularity(fit_alc_exp_imp1)
check_singularity(fit_alc_exp_imp2)
check_singularity(fit_alc_exp_imp3)
check_singularity(fit_alc_exp_imp4)
check_singularity(fit_alc_exp_imp5)

# all FALSE
vif(fit_alc_exp_imp1)
vif(fit_alc_exp_imp2)
vif(fit_alc_exp_imp3)
vif(fit_alc_exp_imp4)
vif(fit_alc_exp_imp5)

# all < 2
check_outliers(fit_alc_exp_imp1)
check_outliers(fit_alc_exp_imp2)
check_outliers(fit_alc_exp_imp3)
check_outliers(fit_alc_exp_imp4)
check_outliers(fit_alc_exp_imp5)

# no outliers (error = Error: `check_model()` not implemented for models of class `lmerModLmerTest` yet.)
#check_model(fit_alc_exp_imp1, check = "all")
#check_model(fit_alc_exp_imp2, check = "all")
#check_model(fit_alc_exp_imp3, check = "all")
#check_model(fit_alc_exp_imp4, check = "all")
#check_model(fit_alc_exp_imp5, check = "all")

skew(df_final$alc_exp)
hist(df_final$alc_exp)

# all looks approximately normal
rm(fit_alc_exp,
   fit_alc_exp_imp1, fit_alc_exp_imp2, fit_alc_exp_imp3, fit_alc_exp_imp4,
   fit_alc_exp_imp5)

#------------------------------------------------------------------------------#
#                 Final Models - Perceptions
#------------------------------------------------------------------------------#

# random effect: family ID nested within site ID
fit_alc_per <- with(
  mids_df_final,
  lmer(formula = alc_per ~ cc_alc + tlfb_age_l + sex + race_4l +
         eth_hisp + income + exp_sub + mh_density + cbcl_scr_syn_external_r +
         cbcl_scr_syn_internal_r + (1 | site_id_l / rel_family_id)))

# summary(fit_alc_per)
# nobs = data present for alc_per
fit_alc_per_summary <- summary(pool(fit_alc_per), conf.int = TRUE) %>%
  rename(estimate = estimate ,
         t.statistic = statistic,
         SE = std.error,
         Lower_CI = `2.5 %`,
         Upper_CI = `97.5 %`) %>%
  mutate_if(is.numeric,
            round,
            digits = 5) %>%
  relocate(term, estimate, Lower_CI, Upper_CI, SE, t.statistic, df, p.value)
fit_alc_per_summary
write.csv(fit_alc_per_summary,'output/fit_alc_per_summary.csv')
rm(fit_alc_per_summary)

# check of model diagnostics with Performance package within each imputation
par(mar=c(1,1,1,1))
fit_alc_per_imp1 <- fit_alc_per$analyses[[1]]
fit_alc_per_imp2 <- fit_alc_per$analyses[[2]]
fit_alc_per_imp3 <- fit_alc_per$analyses[[3]]
fit_alc_per_imp4 <- fit_alc_per$analyses[[4]]
fit_alc_per_imp5 <- fit_alc_per$analyses[[5]]
testDispersion(fit_alc_per_imp1)
testDispersion(fit_alc_per_imp2)
testDispersion(fit_alc_per_imp3)
testDispersion(fit_alc_per_imp4)
testDispersion(fit_alc_per_imp5)

# all non-significant
check_singularity(fit_alc_per_imp1)
check_singularity(fit_alc_per_imp2)
check_singularity(fit_alc_per_imp3)
check_singularity(fit_alc_per_imp4)
check_singularity(fit_alc_per_imp5)

# all FALSE
vif(fit_alc_per_imp1)
vif(fit_alc_per_imp2)
vif(fit_alc_per_imp3)
vif(fit_alc_per_imp4)
vif(fit_alc_per_imp5)

# all < 2
check_outliers(fit_alc_per_imp1)
check_outliers(fit_alc_per_imp2)
check_outliers(fit_alc_per_imp3)
check_outliers(fit_alc_per_imp4)
check_outliers(fit_alc_per_imp5)

# no outliers Error: `check_model()` not implemented for models of class `lmerModLmerTest` yet.
#check_model(fit_alc_per_imp1, check = "all")
#check_model(fit_alc_per_imp2, check = "all")
#check_model(fit_alc_per_imp3, check = "all")
#check_model(fit_alc_per_imp4, check = "all")
#check_model(fit_alc_per_imp5, check = "all")

skew(df_final$alc_per)
hist(df_final$alc_per)

# all looks approximately normal
rm(fit_alc_per,
   fit_alc_per_imp1, fit_alc_per_imp2, fit_alc_per_imp3, fit_alc_per_imp4,
   fit_alc_per_imp5)
   
#------------------------------------------------------------------------------#
#                     Final Models - Cannabis Initiation
#------------------------------------------------------------------------------#

fit_cb_DV <- with(mids_df_final,
                  glm(
                    formula = DV_cb ~ cc_cb +
                      tlfb_age_l + sex + race_4l + eth_hisp + income + exp_sub +
                      mh_density + cbcl_scr_syn_external_r + cbcl_scr_syn_internal_r,
                    family = 'binomial')) #runs

# summary(fit_cb_DV)
# confirmed nobs (n sample size)
# nobs = data present for DV_cb
fit_cb_DV_summary <- summary(pool(fit_cb_DV),
                             conf.int = TRUE, exponentiate = TRUE) %>%
  rename(OR = estimate ,
         t.statistic = statistic,
         SE = std.error,
         Lower_CI = `2.5 %`,
         Upper_CI = `97.5 %`) %>%
  mutate_if(is.numeric,
            round,
            digits = 5) %>%
  relocate(term, OR, Lower_CI, Upper_CI, SE, t.statistic, df, p.value)
fit_cb_DV_summary
write.csv(fit_cb_DV_summary,'output/fit_cb_DV_summary.csv')
rm(fit_cb_DV_summary)

# check of model diagnostics with Performance package within each imputation
par(mar=c(1,1,1,1))
fit_cb_DV_imp1 <- fit_cb_DV$analyses[[1]]
fit_cb_DV_imp2 <- fit_cb_DV$analyses[[2]]
fit_cb_DV_imp3 <- fit_cb_DV$analyses[[3]]
fit_cb_DV_imp4 <- fit_cb_DV$analyses[[4]]
fit_cb_DV_imp5 <- fit_cb_DV$analyses[[5]]

testDispersion(fit_cb_DV_imp1)
testDispersion(fit_cb_DV_imp2)
testDispersion(fit_cb_DV_imp3)
testDispersion(fit_cb_DV_imp4)
testDispersion(fit_cb_DV_imp5)

# all non-significant
check_singularity(fit_cb_DV_imp1)
check_singularity(fit_cb_DV_imp2)
check_singularity(fit_cb_DV_imp3)
check_singularity(fit_cb_DV_imp4)
check_singularity(fit_cb_DV_imp5)

# all FALSE
vif(fit_cb_DV_imp1)
vif(fit_cb_DV_imp2)
vif(fit_cb_DV_imp3)
vif(fit_cb_DV_imp4)
vif(fit_cb_DV_imp5)

# all < 2
check_outliers(fit_cb_DV_imp1)
check_outliers(fit_cb_DV_imp2)
check_outliers(fit_cb_DV_imp3)
check_outliers(fit_cb_DV_imp4)
check_outliers(fit_cb_DV_imp5)

# no outliers (Error in loadNamespace(j <- i[[1L]], c(lib.loc, .libPaths()), versionCheck = vI[[j]]): namespace insight 0.19.7 is already loaded, but >= 0.19.8 is required)
#check_model(fit_cb_DV_imp1, check = "all")
#check_model(fit_cb_DV_imp2, check = "all")
#check_model(fit_cb_DV_imp3, check = "all")
#check_model(fit_cb_DV_imp4, check = "all")
#check_model(fit_cb_DV_imp5, check = "all")

# some issues with binned residuals
br_imp1 <- binned_residuals(fit_cb_DV_imp1)
br_imp2 <- binned_residuals(fit_cb_DV_imp2)
br_imp3 <- binned_residuals(fit_cb_DV_imp3)
br_imp4 <- binned_residuals(fit_cb_DV_imp4)
br_imp5 <- binned_residuals(fit_cb_DV_imp5)
write.csv(br_imp1,'output/br_imp1_cb.csv')
write.csv(br_imp2,'output/br_imp2_cb.csv')
write.csv(br_imp3,'output/br_imp3_cb.csv')
write.csv(br_imp4,'output/br_imp4_cb.csv')
write.csv(br_imp5,'output/br_imp5_cb.csv')

skew(df_final$DV_cb)
hist(df_final$DV_cb)

rm(fit_cb_DV,
   fit_cb_DV_imp1, fit_cb_DV_imp2, fit_cb_DV_imp3, fit_cb_DV_imp4,
   fit_cb_DV_imp5,
   br_imp1, br_imp2, br_imp3, br_imp4, br_imp5)

#------------------------------------------------------------------------------#
#               Final Models - Cannabis Expectancies
#------------------------------------------------------------------------------#

fit_cb_exp <- with(
  mids_df_final,
  lmer(formula = cb_exp ~ cc_cb + tlfb_age_l + sex + race_4l +
         eth_hisp + income + exp_sub + mh_density + cbcl_scr_syn_external_r +
         cbcl_scr_syn_internal_r + (1 | site_id_l / rel_family_id)))


# summary(fit_cb_exp)
# confirmed nobs (n sample size)
# nobs = data present for cb_exp
fit_cb_exp_summary <- summary(pool(fit_cb_exp), conf.int = TRUE) %>%
  rename(estimate = estimate ,
         t.statistic = statistic,
         SE = std.error,
         Lower_CI = `2.5 %`,
         Upper_CI = `97.5 %`) %>%
  mutate_if(is.numeric,
            round,
            digits = 5) %>%
  relocate(term, estimate, Lower_CI, Upper_CI, SE, t.statistic, df, p.value)
fit_cb_exp_summary
write.csv(fit_cb_exp_summary,'output/fit_cb_exp_summary.csv')
rm(fit_cb_exp_summary)

# check of model diagnostics with Performance package within each imputation
par(mar=c(1,1,1,1))
fit_cb_exp_imp1 <- fit_cb_exp$analyses[[1]]
fit_cb_exp_imp2 <- fit_cb_exp$analyses[[2]]
fit_cb_exp_imp3 <- fit_cb_exp$analyses[[3]]
fit_cb_exp_imp4 <- fit_cb_exp$analyses[[4]]
fit_cb_exp_imp5 <- fit_cb_exp$analyses[[5]]
testDispersion(fit_cb_exp_imp1)
testDispersion(fit_cb_exp_imp2)
testDispersion(fit_cb_exp_imp3)
testDispersion(fit_cb_exp_imp4)
testDispersion(fit_cb_exp_imp5)

# all non-significant
check_singularity(fit_cb_exp_imp1)
check_singularity(fit_cb_exp_imp2)
check_singularity(fit_cb_exp_imp3)
check_singularity(fit_cb_exp_imp4)
check_singularity(fit_cb_exp_imp5)

# all FALSE
vif(fit_cb_exp_imp1)
vif(fit_cb_exp_imp2)
vif(fit_cb_exp_imp3)
vif(fit_cb_exp_imp4)
vif(fit_cb_exp_imp5)

# all < 2
check_outliers(fit_cb_exp_imp1)
check_outliers(fit_cb_exp_imp2)
check_outliers(fit_cb_exp_imp3)
check_outliers(fit_cb_exp_imp4)
check_outliers(fit_cb_exp_imp5)

# no outliers Error: `check_model()` not implemented for models of class `lmerModLmerTest` yet.
#check_model(fit_cb_exp_imp1, check = "all")
#check_model(fit_cb_exp_imp2, check = "all")
#check_model(fit_cb_exp_imp3, check = "all")
#check_model(fit_cb_exp_imp4, check = "all")
#check_model(fit_cb_exp_imp5, check = "all")

skew(df_final$cb_exp)
hist(df_final$cb_exp)

# all looks approximately normal
rm(fit_cb_exp,
   fit_cb_exp_imp1, fit_cb_exp_imp2, fit_cb_exp_imp3, fit_cb_exp_imp4,
   fit_cb_exp_imp5)

#------------------------------------------------------------------------------#
#                       Final Models - Perceptions
#------------------------------------------------------------------------------#

fit_cb_per <- with(
mids_df_final,
lmer(formula = cb_per ~ cc_cb + tlfb_age_l + sex + race_4l +
eth_hisp + income + exp_sub + mh_density + cbcl_scr_syn_external_r +
cbcl_scr_syn_internal_r + (1 | site_id_l / rel_family_id)))


# summary(fit_cb_per)
# confirmed nobs (n sample size)
# nobs = data present for cb_per
fit_cb_per_summary <- summary(pool(fit_cb_per), conf.int = TRUE) %>%
  rename(estimate = estimate ,
         t.statistic = statistic,
         SE = std.error,
         Lower_CI = `2.5 %`,
         Upper_CI = `97.5 %`) %>%
  mutate_if(is.numeric,
            round,
            digits = 5) %>%
  relocate(term, estimate, Lower_CI, Upper_CI, SE, t.statistic, df, p.value)
fit_cb_per_summary
write.csv(fit_cb_per_summary,'output/fit_cb_per_summary.csv')
rm(fit_cb_per_summary)

# check of model diagnostics with Performance package within each imputation
par(mar=c(1,1,1,1))
fit_cb_per_imp1 <- fit_cb_per$analyses[[1]]
fit_cb_per_imp2 <- fit_cb_per$analyses[[2]]
fit_cb_per_imp3 <- fit_cb_per$analyses[[3]]
fit_cb_per_imp4 <- fit_cb_per$analyses[[4]]
fit_cb_per_imp5 <- fit_cb_per$analyses[[5]]
testDispersion(fit_cb_per_imp1)
testDispersion(fit_cb_per_imp2)
testDispersion(fit_cb_per_imp3)
testDispersion(fit_cb_per_imp4)
testDispersion(fit_cb_per_imp5)

# all non-significant
check_singularity(fit_cb_per_imp1)
check_singularity(fit_cb_per_imp2)
check_singularity(fit_cb_per_imp3)
check_singularity(fit_cb_per_imp4)
check_singularity(fit_cb_per_imp5)

# all FALSE
vif(fit_cb_per_imp1)
vif(fit_cb_per_imp2)
vif(fit_cb_per_imp3)
vif(fit_cb_per_imp4)
vif(fit_cb_per_imp5)

# all < 2
check_outliers(fit_cb_per_imp1)
check_outliers(fit_cb_per_imp2)
check_outliers(fit_cb_per_imp3)
check_outliers(fit_cb_per_imp4)
check_outliers(fit_cb_per_imp5)

# no outliers Error: `check_model()` not implemented for models of class `lmerModLmerTest` yet.
#check_model(fit_cb_per_imp1, check = "all")
#check_model(fit_cb_per_imp2, check = "all")
#check_model(fit_cb_per_imp3, check = "all")
#check_model(fit_cb_per_imp4, check = "all")
#check_model(fit_cb_per_imp5, check = "all")

# all looks approximately normal
rm(fit_cb_per,
   fit_cb_per_imp1, fit_cb_per_imp2, fit_cb_per_imp3, fit_cb_per_imp4,
   fit_cb_per_imp5)

```
